---
title: "Academics"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
---

```{r, include=FALSE}
source("common_code.R")
```

# Student Status

**Are you a first generation student?** 

```{r}
bns$firstgenplot <- bns$firstgen %>% factor(labels = c("No", "Yes"))
plot_frq(bns$firstgenplot) + xlab("First Generation Student")
```

The vast majority of respondents (94.7% n = 142) are first generation college students with only 8 (5.3%) not being first generation students.

**What is your major at CSU, Chico?**

```{r}
table(tolower(bns$major)) %>% kable(col.names = c("Major", "Frequency")) %>% kable_styling() %>% scroll_box(width = "500px", height = "500px")
```

 <br> 
 **What is your approximate overall Grade Point Average (GPA) for your current degree in progress?** `r emo::ji("star")` 

```{r}
plot_frq(bns$SD2) + xlab("GPA")
```

About a third, or 34.0% (n = 51), of participants reported that their GPA is between 2.51 and 3.0, 32.0% (n = 48) reported that their GPA is between 3.01 and 3.5, and 20.0% (n = 30) reported that their GPA is between 2.01 and 2.5. 12.0% (n = 18) reported that their GPA is above 3.5 and lastly 2.0% (n = 3) reported that their GPA is between 1.51 and 2.0.

**How many units (rounded up) are you enrolled in for the current semester at CSU Chico?** 

```{r}
bns$units_relevel <- bns$SD3_1
bns$units_relevel[bns$units_relevel < 12] <- "0-11"
bns$units_relevel[bns$units_relevel > 12 & bns$units_relevel <= 15] <- "13-15"
bns$units_relevel[bns$units_relevel >= 16] <- "16+"
plot_frq(bns$units_relevel, ylim = c(0,100)) + xlab("Units Enrolled")
```

More than half, or 53.7% (n = 80), of students filling out this survey are enrolled in 13-15 units in the semester of the survey, a quarter of the students (24.2% n = 36) are enrolled in 12 units, and 20.8% (n = 31) are enrolled in 16 or more units.

**If currently enrolled at more than one college, how many units (rounded up) are you enrolled in for the current semester at other colleges (NOT CSU Chico)?**

```{r}
bns$outside_units <- bns$SD4_1
bns$outside_units[bns$outside_units <= 3] <- "1-3"
bns$outside_units[bns$outside_units >= 13] <- "13+"
plot_frq(bns$outside_units, vjust=-0.5,  ylim = c(0,4)) + xlab("Units Enrolled Outside CSU Chico")
```

Out of the students who reported they are taking units outside of CSU Chico, about 37.5% (n = 3) are taking 13 or more units in a different college, 25.0% (n = 2) are taking either 1-3 units or 12 units respectively, and only 1 person (12.5%) is enrolled in 10 units outside of CSU Chico.

























