---
title: "Basic Needs Status"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
---

```{r, include=FALSE}
source("common_code.R")
```

# Housing

```{r}
test1 <- as.data.frame(table(bns$SD10))
test2 <- as.data.frame(prop.table(table(bns$SD10)))
finaltest <- left_join(test1, test2, by = "Var1")
names(finaltest) <- c("Housing Situation", "n", "%")
finaltest$`%` <- round(finaltest$`%` * 100, 2)
finaltest %>% kable() %>% kable_styling()
```

# USDA Food Security Questions

* **“In the last 12 months, the food that (I/we) bought just didn’t last, and (I/we) didn’t have money to get more.” Was that often, sometimes, or never true for (you/your household)?**

```{r}
plot_frq(bns$HH3) + xlab("Food Didn't Last + No Money to Get More")
```

Over half of respondents, or 54.3%, said it is sometimes true that in the last 12 months, the food that was bought didn't last and they didn't have money to get more. 21.4% of respondents said that was often true. 

* **“In the last 12 months, (I/we) couldn’t afford to eat balanced meals.” Was that often, sometimes, or never true for (you/your household)?**

```{r}
plot_frq(bns$HH4) + xlab("Couldn't Afford Balanced Meals")
```

Over half of respondents, or 52.1%, said it is sometimes true that in the last 12 months, they couldn't afford to eat balanced meals. 23.2% of respondents said that was often true. 

* **In the last 12 months, did you or other adults in your household, ever cut the size of your meals or skip meals because there wasn’t enough money for food?** 

```{r}
plot_frq(bns$AD1) + xlab("Cut Size/Skip Meals Because No Money")
```

Over half of respondents, or 58%, reported that they, or the other adults in their household, cut the size of their meals, or skipped meals, because there was not enough money for food. 

* *How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?*

```{r}
plot_frq(bns$AD1a) + xlab("Cut Size/Skip Meals Because No Money")
```

Of the respondents that answered yes to cutting the size of their meals, or skipping meals, over half (54.5%) said this happened some months but not every month. 27.3% reported this happened almost every month. 

* **In the last 12 months, did you ever eat less than you felt you should because there was not enough money for food?**

```{r}
plot_frq(bns$AD2) + xlab("Ate Less Because Not Enough Money")
```

The majority of respondents, or 61.8%, reported eating less then they felt they should over the last 12 months because there was not enough money for food. 

* *How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?*

```{r}
plot_frq(bns$AD2a) + xlab("Ate Less Because Not Enough Money")
```

Of those that responded yes that they ate less because there was not enough money for food, about half (50.6%) reported this happened some months but not every month. 24.7% of respondents reported this happened almost every month. 

* **In the last 12 months, were you ever hungry but you did not eat because there wasn’t enough money for food?**

```{r}
plot_frq(bns$AD3) + xlab("Hungry Because Not Eating Due to Money")
```

Over half of respondents, or 54.5%, reported that there were times they were hungry but did not eat because there wasn't enough money for food. 

* *How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?*

```{r}
plot_frq(bns$AD3a) + xlab("Hungry Because Not Eating Due to Money")
```

Of those that responded yes they were hungry but did not eat because lack of money for food, more than half, or 55.3%, reported this happened some months but not every month. 22.4% of respondents reported this happened almost every month.

* **In the last 12 months, did you lose weight because there wasn’t enough money for food?**

```{r}
plot_frq(bns$AD4) + xlab("Lose Weight Because No Money for Food")
```
Most respondents (67.4%) reported they did not lose weight because there wasn't enough money for food. 
 
* **In the last 12 months, did (you/you or other adults in your household) ever not eat for a whole day because there wasn’t enough money for food?** 

```{r}
plot_frq(bns$AD5) + xlab("Adults did not Eat Because No Money")
```

Most respondents (74.8%) reported that none of the adults in their household ever went a whole day without eating because there wasn't enough money for food. 

* *How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?*

```{r}
plot_frq(bns$AD5a) + xlab("Adults did not Eat Because No Money") + ylim(c(0,20))
```

Out of the 34 respondents that answered yes, either they or their adult household member went a whole day without eating because there wasn't enough money for food, over half (51.6%) reported this happened some months but not every month. 22.6% reported this happened every month.  

## Food Insecure

Food insecurity is defined by meeting 2 or more of the following criteria:

*Selecting sometimes true or often true for not having enough food or money to last and not being able to afford balanced meals. 

*Selecting yes for any of the 5 prior bulleted, bold questions.

```{r}
bns$food_insecurity <- factor(bns$food_insecurity, labels = c("No", "Yes"))
plot_frq(bns$food_insecurity) + xlab("Food Insecure")
```

The majority of respondents, or 65.3%, reported that yes, they were food insecure in the last 12 months. 34.7% reported that no, they were not food insecure. 

# Mental Health

**How many days in the past month have you experienced heightened anxiety, stress, depression and/or problems with emotions?**

```{r}
bns$MH1_1[bns$MH1_1 >= 15 & bns$MH1_1 < 30] <- "15-29"
bns$MH1_1[bns$MH1_1 >= 30] <- "30+"

plot_frq(bns$MH1_1) + xlab("# of Days") + ylab("Count")
```

**By Gender Identity**

All but three respondents selected either Male or Female for their gender identity. Their response distribution is below. 

```{r, fig.width=12, fig.height=5}
toplot <- bns %>% filter(D4 %in% c('Man', 'Woman'))
plot_xtab(x=toplot$MH1_1, grp=toplot$D4, margin="col", show.total = FALSE) + 
          xlab("# of Days") + ylab("Percent (count)") + 
          theme(legend.position="top", legend.title=element_blank()) 

```

```{r, eval=FALSE}
bns$MH1_1[bns$D4=="Gender Queer or Gender-Nonconforming"]
bns$MH1_1[bns$D4=="Gender unlisted:"]
```

* Two respondents selected `Gender Queer or Gender-Nonconforming`, one reported `15-29` days, the other `30+` days. 
* The one respondent who selected `Gender Unlisted` reported `10` days. 

## Mental Health Services

**Have you received or tried to receive mental health services over the past 12months?**

```{r}
plot_frq(bns$MH2) + xlab("Received Mental Health Services") + ylim(c(0,100))
```

Over half of the respondents, or 58.9%, answered no when asked if they had received, or tried to receive, mental health services over the past 12 months. 






















