---
title: "Participation in Basic Needs Programs and Services"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(ggplot2)
library(sjPlot)
library(kableExtra)
library(knitr)
library(dplyr)
library(tidyverse)

load("../data/bns_clean.Rdata")
bns <- out

opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, cache=FALSE, fig.height=4, fig.width=6, fig.align = 'center')
# don't forget when done with session to turn CACHE = FALSE and clear knitr cache (last option under the knit button)

# Helper functions to display text answers without blank lines
display.text <- function(data, var){
  data %>% filter(!!as.symbol(var)!="") %>% select(!!as.symbol(var)) %>%
           kable(col.names=NULL) %>% 
           kable_styling(full_width = FALSE, 
           bootstrap_options =c("striped", "responsive", "hover", "condensed"))
}

sjPlot::set_theme(base = theme_bw())
```

## Participation in Programs `r emo::ji("star")`

### CalFresh(also known as Food Stamps or SNAP benefits)

```{r}
plot_frq(bns$SRC1_1) + xlab("CalFresh")
```

50.0% (n = 74) of respondents reported that they currently CalFresh and 17.6% (n = 26) have used it in the past. 31.1% (n = 46) reported they have heard of CalFresh but have never used it and 1.4% (n = 2) have never heard of it.

### Women, Infant and Children (WIC) nutrition program 

```{r}
plot_frq(bns$SRC1_2) + xlab("WIC Program")
```

Only 2.7% (n = 4) of respondents reported they currently use the WIC nutrition program, 6.8% (n = 10) of respondents reported they have used it in the past, and 17.0% (n = 25) reported they have never heard of it. The majority (n = 108 73.5%) reported that they have heard of it but never have used it.

### CalWORKS (also known as Cash Aid or Welfare)

```{r}
plot_frq(bns$SRC1_3) + xlab("CalWORKS")
```

Only 0.7% (n = 1) of respondents reported they currently use CalWORKS, 6.8% (n = 10) of respondents reported they have used it in the past, and 7.4% (n = 11) reported they have never heard of it. The majority (n = 126 85.1%) reported that they have heard of it but never have used it.

### Emergency food from food bank, food pantry, or church

```{r}
plot_frq(bns$SRC1_4) + xlab("Emergency Food (Food Pantry)")
```

28.4% (n = 42) of respondents reported that they currently use emergency food from the food bank, food pantry, or church, 28.4% (n = 42) reported they have used emergency food in the past, and 3.4% (n = 5) reported they never heard of it. The majority (n = 59 39.9%) reported they have heard of it but never used it.

### Free food from other community organization (meal vouchers, bag of groceries, gleaned produce, etc.)

```{r}
plot_frq(bns$SRC1_5) + xlab("Free Food (Meal Vouchers)")
```

9.5% (n = 14) of respondents reported that they currently get free food from other community organizations such as meal vouchers, 15.5% (n = 23) reported they have used it in the past, and 22.3% (n = 33) reported they have never heard of it. The majority (n = 78 52.7%) reported that they have heard of it but have never used it.

### Free or reduced lunch meals at district schools for my children and/or dependents

```{r}
plot_frq(bns$SRC1_6) + xlab("Free/Reduced Lunch")
```

6.8% (n = 10) of respondents reported that they currently have free or reduced lunch meals at district schools for theit children or dependents, 45.3% (n = 67) reported that they have in the past, and 37.2% (n = 55) reported they have heard of it but have never used it. Only 10.8% (n = 16) reported they have never heard of it.

## Check all statements below that apply to you while you receive or received CalFresh benefits `r emo::ji("star")`

### I am/was able to work or worked fewer hours each week in a PAID position.

```{r}
plot_frq(bns$SRC1a_1) + xlab("Work in Paid Position")
```

29.0% (n = 29) of respondents agreed that they are/were able to work fewer hours in a paid position when they received CalFresh benefits and 17.0% (n = 17) disagreed with the statement. 25.0% (n = 25) neither agreed nor disagreed.

### I have/had more time to do an UNPAID internship or volunteer work.

```{r}
plot_frq(bns$SRC1a_2) + xlab("More Time for Unpaid Work")
```

20.0% (n = 20) of respondents agreed that they had more time for unpaid work when they received CalFresh benefits and 26.0% (n = 26) disagreed with the statement. 33.0% (n = 33) neither agreed or disagreed.

### I have/had more money to pay for bills (rent, utility bills, clothes, etc.)

```{r}
plot_frq(bns$SRC1a_3) + xlab("More Money for Bills")
```

35.0% (n = 35) of respondents agreed that they had more money to pay bills when they received CalFresh benefits and 18.0% (n = 18) disagreed with the statement. 20.0% (n = 20) neither agreed or disagreed.

### I have/had more money for entertainment and social activities(ex. attending movies, shopping, and bars or parties, etc.)

```{r}
plot_frq(bns$SRC1a_4) + xlab("More Money for Entertainment") + ylim(c(0,35))
```

31.0% (n = 31) of respondents agreed that they had more money for entertainment and social activities when they received CalFresh benefits and 25.0% (n = 25) disagreed with the statement. 25.0% (n = 20) neither agreed or disagreed.

### I am/was able to shop/shopped more frequently at the farmers’ market.

```{r}
plot_frq(bns$SRC1a_5) + xlab("Farmers' Market") + ylim(c(0,35))
```

23.0% (n = 23) of respondents agreed that they were able to shop more at the farmers' market when they received CalFresh benefits and 24.0% (n = 24) disagreed with the statement. 27.0% (n = 27) neither agreed or disagreed.

### I have/had learned more about healthier foods.

```{r}
plot_frq(bns$SRC1a_6) + xlab("Learned More about Healthy Foods")
```

48.0% (n = 48) of respondents agreed that they learned more about healthier foods when they received CalFresh benefits and 9.0% (n = 9) disagreed with the statement. 15.0% (n = 15) neither agreed or disagreed.

### I am/was able to purchase/purchased healthier foods.

```{r}
plot_frq(bns$SRC1a_7) + xlab("Purchase Healthier Foods")
```

40.0% (n = 40) of respondents agreed that they were able to purchase healthier foods when they received CalFresh benefits and 4.0% (n = 4) disagreed with the statement. 15.0% (n = 15) neither agreed or disagreed.

### I cook/cooked more frequently at home.

```{r}
plot_frq(bns$SRC1b_1) + xlab("Cook More Frequently at Home")
```

40.0% (n = 40) of respondents agreed that they were able to cook more frequently at home when they received CalFresh benefits and 2.0% (n = 2) disagreed with the statement. 7.0% (n = 7) neither agreed or disagreed.

### I consume/consumed a healthier diet.

```{r}
plot_frq(bns$SRC1b_2) + xlab("Healthier Diet")
```

45.0% (n = 45) of respondents agreed that were able to consume a healthier diet when they received CalFresh benefits and 7.0% (n = 7) disagreed with the statement. 14.0% (n = 14) neither agreed or disagreed.

### I consume/consumed less fast food.

```{r}
plot_frq(bns$SRC1b_3) + xlab("Less Fast Food")
```

44.0% (n = 44) of respondents agreed that they eat less fast food when they received CalFresh benefits and 9.0% (n = 9) disagreed with the statement. 11.0% (n = 11) neither agreed or disagreed.

### I consume/consumed fewer processed foods.

```{r}
plot_frq(bns$SRC1b_4) + xlab("Less Processed Foods")
```

38.0% (n = 38) of respondents agreed that they eat less processed foods when they received CalFresh benefits and 7.0% (n = 7) disagreed with the statement. 23.0% (n = 23) neither agreed or disagreed.

### I consume/consumed fewer sugar-sweetened beverages like soda and energy drinks.

```{r}
plot_frq(bns$SRC1b_5) + xlab("Fewer Sugar-Sweetened Beverages")
```

37.0% (n = 37) of respondents agreed that they drink fewer sugar-sweetened drinks when they received CalFresh benefits and 11.0% (n = 11) disagreed with the statement. 17.0% (n = 17) neither agreed or disagreed.

### I consume/consumed less alcohol or fewer alcoholic beverages.

```{r}
plot_frq(bns$SRC1b_6) + xlab("Less Alcoholic Beverages")
```

29.0% (n = 29) of respondents agreed that they drink fewer alcoholic drinks when they received CalFresh benefits and 9.0% (n = 9) disagreed with the statement. 28.0% (n = 28) neither agreed or disagreed.

### I enroll/enrolled in more classes.

```{r}
plot_frq(bns$SRC1c_1) + xlab("Enrolled in More Classes")
```

38.0% (n = 38) of respondents agreed that they enrolled in more classes when they received CalFresh benefits and 9.0% (n = 9) disagreed with the statement. 39.0% (n = 39) neither agreed or disagreed.





