---
title: "Participation in Basic Needs Programs and Services"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(ggplot2)
library(sjPlot)
library(kableExtra)
library(knitr)
library(dplyr)
library(tidyverse)

load("../data/bns_clean.Rdata")
bns <- out

opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, cache=FALSE, fig.height=4, fig.width=6, fig.align = 'center')
# don't forget when done with session to turn CACHE = FALSE and clear knitr cache (last option under the knit button)

# Helper functions to display text answers without blank lines
display.text <- function(data, var){
  data %>% filter(!!as.symbol(var)!="") %>% select(!!as.symbol(var)) %>%
           kable(col.names=NULL) %>% 
           kable_styling(full_width = FALSE, 
           bootstrap_options =c("striped", "responsive", "hover", "condensed"))
}

sjPlot::set_theme(base = theme_bw())
```

## Participation in Programs `r emo::ji("star")` `r emo::ji("pencil")`

### CalFresh(also known as Food Stamps or SNAP benefits)

```{r}
plot_frq(bns$SRC1_1) + xlab("CalFresh")
```

50.0% (n = 74) of respondents reported that they currently CalFresh and 17.6% (n = 26) have used it in the past. 31.1% (n = 46) reported they have heard of CalFresh but have never used it and 1.4% (n = 2) have never heard of it.

### Women, Infant and Children (WIC) nutrition program 

```{r}
plot_frq(bns$SRC1_2) + xlab("WIC Program")
```

Only 2.7% (n = 4) of respondents reported they currently use the WIC nutrition program, 6.8% (n = 10) of respondents reported they have used it in the past, and 17.0% (n = 25) reported they have never heard of it. The majority (n = 108 73.5%) reported that they have heard of it but never have used it.

### CalWORKS (also known as Cash Aid or Welfare)

```{r}
plot_frq(bns$SRC1_3) + xlab("CalWORKS")
```

Only 0.7% (n = 1) of respondents reported they currently use CalWORKS, 6.8% (n = 10) of respondents reported they have used it in the past, and 7.4% (n = 11) reported they have never heard of it. The majority (n = 126 85.1%) reported that they have heard of it but never have used it.

### Emergency food from food bank, food pantry, or church

```{r}
plot_frq(bns$SRC1_4) + xlab("Emergency Food (Food Pantry)")
```

28.4% (n = 42) of respondents reported that they currently use emergency food from the food bank, food pantry, or church, 28.4% (n = 42) reported they have used emergency food in the past, and 3.4% (n = 5) reported they never heard of it. The majority (n = 59 39.9%) reported they have heard of it but never used it.

### Free food from other community organization (meal vouchers, bag of groceries, gleaned produce, etc.)

```{r}
plot_frq(bns$SRC1_5) + xlab("Free Food (Meal Vouchers)")
```

9.5% (n = 14) of respondents reported that they currently get free food from other community organizations such as meal vouchers, 15.5% (n = 23) reported they have used it in the past, and 22.3% (n = 33) reported they have never heard of it. The majority (n = 78 52.7%) reported that they have heard of it but have never used it.

### Free or reduced lunch meals at district schools for my children and/or dependents

```{r}
plot_frq(bns$SRC1_6) + xlab("Free/Reduced Lunch")
```

6.8% (n = 10) of respondents reported that they currently have free or reduced lunch meals at district schools for theit children or dependents, 45.3% (n = 67) reported that they have in the past, and 37.2% (n = 55) reported they have heard of it but have never used it. Only 10.8% (n = 16) reported they have never heard of it.

## Check all statements below that apply to you while you receive or received CalFresh benefits `r emo::ji("star")`
<!---
### I am/was able to work or worked fewer hours each week in a PAID position.

```{r}
plot_frq(bns$SRC1a_1) + xlab("Work in Paid Position")
```

29.0% (n = 29) of respondents agreed that they are/were able to work fewer hours in a paid position when they received CalFresh benefits and 17.0% (n = 17) disagreed with the statement. 25.0% (n = 25) neither agreed nor disagreed.

### I have/had more time to do an UNPAID internship or volunteer work.

```{r}
plot_frq(bns$SRC1a_2) + xlab("More Time for Unpaid Work")
```

20.0% (n = 20) of respondents agreed that they had more time for unpaid work when they received CalFresh benefits and 26.0% (n = 26) disagreed with the statement. 33.0% (n = 33) neither agreed nor disagreed.

### I have/had more money to pay for bills (rent, utility bills, clothes, etc.)

```{r}
plot_frq(bns$SRC1a_3) + xlab("More Money for Bills")
```

35.0% (n = 35) of respondents agreed that they had more money to pay bills when they received CalFresh benefits and 18.0% (n = 18) disagreed with the statement. 20.0% (n = 20) neither agreed nor disagreed.

### I have/had more money for entertainment and social activities(ex. attending movies, shopping, and bars or parties, etc.)

```{r}
plot_frq(bns$SRC1a_4) + xlab("More Money for Entertainment") + ylim(c(0,35))
```

31.0% (n = 31) of respondents agreed that they had more money for entertainment and social activities when they received CalFresh benefits and 25.0% (n = 25) disagreed with the statement. 25.0% (n = 20) neither agreed nor disagreed.

### I am/was able to shop/shopped more frequently at the farmers’ market.

```{r}
plot_frq(bns$SRC1a_5) + xlab("Farmers' Market") + ylim(c(0,35))
```

23.0% (n = 23) of respondents agreed that they were able to shop more at the farmers' market when they received CalFresh benefits and 24.0% (n = 24) disagreed with the statement. 27.0% (n = 27) neither agreed nor disagreed.

### I have/had learned more about healthier foods.

```{r}
plot_frq(bns$SRC1a_6) + xlab("Learned More about Healthy Foods")
```

48.0% (n = 48) of respondents agreed that they learned more about healthier foods when they received CalFresh benefits and 9.0% (n = 9) disagreed with the statement. 15.0% (n = 15) neither agreed nor disagreed.

### I am/was able to purchase/purchased healthier foods.

```{r}
plot_frq(bns$SRC1a_7) + xlab("Purchase Healthier Foods")
```

40.0% (n = 40) of respondents agreed that they were able to purchase healthier foods when they received CalFresh benefits and 4.0% (n = 4) disagreed with the statement. 15.0% (n = 15) neither agreed nor disagreed.

### I cook/cooked more frequently at home.

```{r}
plot_frq(bns$SRC1b_1) + xlab("Cook More Frequently at Home")
```

40.0% (n = 40) of respondents agreed that they were able to cook more frequently at home when they received CalFresh benefits and 2.0% (n = 2) disagreed with the statement. 7.0% (n = 7) neither agreed nor disagreed.

### I consume/consumed a healthier diet.

```{r}
plot_frq(bns$SRC1b_2) + xlab("Healthier Diet")
```

45.0% (n = 45) of respondents agreed that were able to consume a healthier diet when they received CalFresh benefits and 7.0% (n = 7) disagreed with the statement. 14.0% (n = 14) neither agreed nor disagreed.

### I consume/consumed less fast food.

```{r}
plot_frq(bns$SRC1b_3) + xlab("Less Fast Food")
```

44.0% (n = 44) of respondents agreed that they eat less fast food when they received CalFresh benefits and 9.0% (n = 9) disagreed with the statement. 11.0% (n = 11) neither agreed nor disagreed.

### I consume/consumed fewer processed foods.

```{r}
plot_frq(bns$SRC1b_4) + xlab("Less Processed Foods")
```

38.0% (n = 38) of respondents agreed that they eat less processed foods when they received CalFresh benefits and 7.0% (n = 7) disagreed with the statement. 23.0% (n = 23) neither agreed nor disagreed.

### I consume/consumed fewer sugar-sweetened beverages like soda and energy drinks.

```{r}
plot_frq(bns$SRC1b_5) + xlab("Fewer Sugar-Sweetened Beverages")
```

37.0% (n = 37) of respondents agreed that they drink fewer sugar-sweetened drinks when they received CalFresh benefits and 11.0% (n = 11) disagreed with the statement. 17.0% (n = 17) neither agreed nor disagreed.

### I consume/consumed less alcohol or fewer alcoholic beverages.

```{r}
plot_frq(bns$SRC1b_6) + xlab("Less Alcoholic Beverages")
```

29.0% (n = 29) of respondents agreed that they drink fewer alcoholic drinks when they received CalFresh benefits and 9.0% (n = 9) disagreed with the statement. 28.0% (n = 28) neither agreed nor disagreed.

### I enroll/enrolled in more classes.

```{r}
plot_frq(bns$SRC1c_1) + xlab("Enrolled in More Classes")
```

38.0% (n = 38) of respondents agreed that they enrolled in more classes when they received CalFresh benefits and 9.0% (n = 9) disagreed with the statement. 39.0% (n = 39) neither agreed nor disagreed.

### I concentrate/concentrated more in class(es)

```{r}
plot_frq(bns$SRC1c_2) + xlab("Concentrated in Class")
```

55.0% (n = 55) of respondents agreed that they concentrated more in classes when they received CalFresh benefits and 3.0% (n = 3) disagreed with the statement. 20.0% (n = 20) neither agreed nor disagreed.

### My grades have/had improved

```{r}
plot_frq(bns$SRC1c_3) + xlab("Grades Improved")
```

41.0% (n = 41) of respondents agreed that their grades improved when they received CalFresh benefits and 2.0% (n = 2) disagreed with the statement. 36.0% (n = 36) neither agreed nor disagreed.

### I have/had more time to study for exams and quizzes

```{r}
plot_frq(bns$SRC1c_4) + xlab("More Time to Study for Exams")
```

41.0% (n = 41) of respondents agreed that they had more time to study for exams and quizzes when they received CalFresh benefits and 4.0% (n = 4) disagreed with the statement. 34.0% (n = 34) neither agreed nor disagreed.

### I have/had more time to read course materials or prepare for the next class`

```{r}
plot_frq(bns$SRC1c_5) + xlab("More Time to Read/Prepare for Class")
```

42.4% (n = 42) of respondents agreed that they had more time to read and prepare for their next class when they received CalFresh benefits and 5.1% (n = 5) disagreed with the statement. 33.3% (n = 33) neither agreed nor disagreed.

### I have/had more time to finish homework or course assignments and activities

```{r}
plot_frq(bns$SRC1c_6) + xlab("More Time to Finish Homework/Activities")
```

41.0% (n = 41) of respondents agreed that they had more time to finish homework and other course assignments when they received CalFresh benefits and 5.0% (n = 5) disagreed with the statement. 32.0% (n = 32) neither agreed nor disagreed.

### I have/had more time to go to my professors’office hours when needed

```{r}
plot_frq(bns$SRC1c_7) + xlab("More Time to Go to Office Hours")
```

38.0% (n = 38) of respondents agreed that they had more time to go to their professors' office hours when they received CalFresh benefits and 8.0% (n = 8) disagreed with the statement. 35.0% (n = 35) neither agreed nor disagreed.

### I have/had more time to attend all classes as they are scheduled

```{r}
plot_frq(bns$SRC1c_8) + xlab("More Time to Attend All Classes")
```

39.4% (n = 39) of respondents agreed that they had more time to attend all their classes as they are scheduled when they received CalFresh benefits and 4.0% (n = 4) disagreed with the statement. 34.3% (n = 34) neither agreed nor disagreed.

### I have/had more time to go on field trips or field work placements

```{r}
plot_frq(bns$SRC1c_9) + xlab("More Time to Go on Field Trips")
```

31.0% (n = 31) of respondents agreed that they had more time to go on field trips or field work placements when they received CalFresh benefits and 8.0% (n = 8) disagreed with the statement. 42.0% (n = 42) neither agreed nor disagreed.

### My sleep quality has/had improved

```{r}
plot_frq(bns$SRC1c_10) + xlab("Sleep Quality Improved")
```

39.4% (n = 39) of respondents agreed that their sleep quality improved when they received CalFresh benefits and 10.1% (n = 10) disagreed with the statement. 26.3% (n = 26) neither agreed nor disagreed.

### My stress level has/had decreased. (ex. I’m not stressed about having money for food or bills)

```{r}
plot_frq(bns$SRC1c_11) + xlab("Stress Levels Decreased")
```

34.0% (n = 34) of respondents agreed that their stress levels decreased when they received CalFresh benefits and 9.0% (n = 9) disagreed with the statement. 14.0% (n = 14) neither agreed nor disagreed. Additionally, 35.0% (n = 35) strongly agreed that their stress levels decreased.
--->

```{r}
src1 <- bns %>% select(starts_with("SRC1a_"))
names(src1) <- c("Fewer Hours Paid", "More Time for Unpaid", "More Money for Bills", "More Money for Entertainment", "Shop More at Farmers' Market", "Learned More about Healthy Foods", "Able to Purchase Healthy Foods")
plot_likert(src1, 
            grid.range = c(1.2, 1.4),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE) + theme_bw()
```

```{r}
src2 <- bns %>% select(starts_with("SRC1b_"))
names(src2) <- c("Cook at Home", "Consumed Healthier Diet", "Consumed Less Fast Food", "Consumed Fewer Processed Foods", "Consumed Fewer Sweetened Drinks", "Consumed Fewer Alcoholic Beverages")
plot_likert(src2, 
            grid.range = c(1.2, 1.4),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE) + theme_bw()
```


```{r}
src3 <- bns %>% select(starts_with("SRC1c_"))
names(src3) <- c("Enrolled in More Classes",
                 "Concentrated More in Classes",
                 "Grades Improved",
                 "More Time to Study for Exams",
                 "More Time to Prepare for Class",
                 "More Time for Homework",
                 "More Time for Office Hours",
                 "More Time for Field Trips",
                 "Sleep Quality Improved",
                 "Stress Level Decreased")
plot_likert(src3, 
            grid.range = c(1.2, 1.4),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE) + theme_bw()
```

# Barriers to CalFresh `r emo::ji("star")`

barrier_toolong
barrier_toodiff
barrier_campusnothelpful
bns$barrier_countynotsupportive
barrier_verif
barrier_office
barrier_transportation
barrier_eligible
barrier_family
barrier_embarrassed
barrier_belief
barrier_need
barrier_other

# Temporary Home for Questions `r emo::ji("pencil")`

## At any time in the last 12 months, have you utilized campus food pantries or local food banks for food? 
```{r}
plot_frq(bns$SRC2, vjust = "center", y.offset = 4) + coord_flip() + xlab("Utilized Campus Food Pantries")
```

## “In the last 12 months, the food that (I/we) bought just didn’t last, and (I/we) didn’t have money to get more.” Was that often, sometimes,or nevertrue for (you/your household)?

```{r}
plot_frq(bns$HH3) + xlab("Food Didn't Last + No Money to Get More")
```

## “In the last 12 months, (I/we) couldn’t afford to eat balanced meals.” Was that often, sometimes, or never true for (you/your household)?

```{r}
plot_frq(bns$HH4) + xlab("Couldn't Afford Balanced Meals")
```

## In the last 12 months, did you or other adults in your household,ever cut the size of your meals or skip meals because there wasn’t enough money for food?

```{r}
plot_frq(bns$AD1) + xlab("Cut Size/Skip Meals Because No Money")
```

## How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?

```{r}
plot_frq(bns$AD1a) + xlab("Cut Size/Skip Meals Because No Money")
```

## In the last 12 months, did you ever eat less than you felt you should because there was not enough money for food?

```{r}
plot_frq(bns$AD2) + xlab("Ate Less Because Not Enough Money")
```

## How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?

```{r}
plot_frq(bns$AD2a) + xlab("Ate Less Because Not Enough Money")
```

## In the last 12 months, were you ever hungry but you did not eat because there wasn’t enough money for food?

```{r}
plot_frq(bns$AD3) + xlab("Hungry Because Not Eating Due to Money")
```

## How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?

```{r}
plot_frq(bns$AD3a) + xlab("Hungry Because Not Eating Due to Money")
```

## In the last 12 months, did you lose weight because there wasn’t enough money for food?

```{r}
plot_frq(bns$AD4) + xlab("Lose Weight Because No Money for Food")
```

## In the last 12 months, did (you/you or other adults in your household) ever not eat for a whole day because there wasn’t enough money for food? 

```{r}
plot_frq(bns$AD5) + xlab("Adults did not Eat Because No Money")
```

## How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?

```{r}
plot_frq(bns$AD5a) + xlab("Adults did not Eat Because No Money") + ylim(c(0,20))
```

## Food Insecure

```{r}
bns$food_insecurity <- factor(bns$food_insecurity, labels = c("No", "Yes"))
plot_frq(bns$food_insecurity) + xlab("Food Insecure")
```











