---
title: "Demographics"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(ggplot2)
library(sjPlot)
library(kableExtra)
library(knitr)
library(dplyr)
library(tidyverse)

load("../data/bns_clean.Rdata")
bns <- out

opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, cache=FALSE, fig.height=4, fig.width=6, fig.align = 'center')
# don't forget when done with sessino to turn CACHE = FALSE and clear knitr cache (last option under the knit button)

# Helper functions to display text answers without blank lines
display.text <- function(data, var){
  data %>% filter(!!as.symbol(var)!="") %>% select(!!as.symbol(var)) %>%
           kable(col.names=NULL) %>% 
           kable_styling(full_width = FALSE, 
           bootstrap_options =c("striped", "responsive", "hover", "condensed"))
}

sjPlot::set_theme(base = theme_bw())
```

# Gender `r emo::ji("star")` 

### The US Census lists the following choices for sex: Male Female. Please choose the one that most closely fits your identity. `r emo::ji("pencil")`

```{r}
plot_frq(bns$D2) + xlab("Sex")
```

70% of the respondents (n = 105) are Female and 30% of the respondents (n = 45) are Male.

### What was your sex assigned at birth? `r emo::ji("pencil")`

```{r}
plot_frq(bns$D3, ylim = c(0,130)) + xlab("Sex")
```

70.7% of the respondents (n = 106) were Female at birth and 29.3% of the respondents (n = 44) were Male at birth.

### What is your gender identity? `r emo::ji("pencil")`

```{r}
plot_frq(bns$D4) + xlab("Gender Identity")
```

69.3 % of the respondents identify as a Woman (n = 104), 28.7% identify as a Man (n = 43), and lastly 1.3% (n = 2) identify as Gender Queer or Gender-Nonconforming.

# Race / Ethnicity `r emo::ji("star")`

### How do you identify your race? `r emo::ji("pencil")`

```{r}
plot_frq(bns$D5, wrap.labels = 10) + xlab("Race")
```

A majority of the respondents did not list their race (48.2% n = 68). 22.0% (n = 31) of the respondents identified as white, followed by 9.9% (n = 14) of the respondents identified as Black or African American. 9.9% (n = 14) of the respondents identified as Mixed race, and 7.8% (n = 11) identified as Asian. Lastly, 1.4% (n = 2) identified as American Indian or Alaska Native, and 0.7% (n = 1) identified as Native Hawaiian or other Pacific Islander.

### How do you identify your ethnicity? `r emo::ji("pencil")`

```{r}
plot_frq(bns$D6) + xlab("Ethnicity")
```

74.7% (n = 109) of respondents identified as Hispanic or Latino and 25.3% (n = 37) identified as Non-Hispanic or Latino.

# Marital Status

### What is your marital status? `r emo::ji("pencil")`

```{r}
plot_frq(bns$D7) + xlab("Marital Status")
```

A large proportion (88.5% n = 131) of the respondents reported that they are single and have never been married. 6.1% (n = 9) reporter they are married, 4.0% (n = 6) reported they are living with a partner, 0.7% (n = 1) reported they are separated, and lastly 0.7% (n = 1) reported they are widowed.

# Citizenship

### Are you a US citizen?

```{r}
plot_frq(bns$D8) + xlab("Citizenship Status")
```

92.6% (n = 137) of respondents reported that they are U.S. citizens and 7.4% (n = 11) reported they are not citizens.

### If not a U.S. citizen, are you a lawful permanent resident (i.e. have a “green card”)?

```{r}
plot_frq(bns$D8a, ylim = c(0,8)) + xlab("Permanent Resident")
```

Out of the participants that were not a U.S. citizen, 54.5% (n = 6) report they are not a permanent resident and 45.5% (n = 5) report they are a permanent resident.

# Dependents

### How many dependents receive more than 50% of their financial support from you? `r emo::ji("pencil")`

```{r}
bns$dependents_relevel <- bns$D9_1
bns$dependents_relevel[bns$dependents_relevel >= "2"] <- "2+"
plot_frq(bns$dependents_relevel) + xlab("Number of Dependents")
```

88.0% (n = 132) of participants report that they have 0 dependents who receive more than 50% of their financial support from them. 6.0% (n = 9) report that they have 1 dependent and 6.0% (n = 9) report that they have 2 or more dependents.

### What is/are the age(s) of your dependent(s)?

```{r}
a <- bns %>% 
  summarise_at(vars(contains("age_dep_")), sum) %>%
  t() %>% data.frame()
names(a) <- "N"
a$lab <- paste0(a$N, " (", round(a$N/NROW(bns)*100,0), ")%")
a$type <- stringr::str_replace(rownames(a), "age_dep_", "")
a$type <- factor(a$type)
a$type <- a$type %>% fct_relevel(levels = c("lt5", "6_12", "13_18", "19_60", "over61"))
a$type <- factor(a$type, labels = c("0-5", "6-12", "13-18", "19-60", "61+"))
ggplot(a, aes(x=type, y=N)) + geom_col(fill="#336699") +  
        geom_text(aes(label=lab, y=N+2)) + xlab("Age of Dependents") +
        scale_y_continuous(limits=c(0,10)) + 
        coord_flip()
```

About 5% (n = 8) of the total number of respondents say they have dependents that are between 6-12 years old, 5% (n = 7) say they have dependents that are between 19-60 years old, and only 1 person says they have dependents that are over 61 years old.

# Student Status

### Are you a first generation student? `r emo::ji("pencil")`

```{r}
bns$firstgenplot <- bns$firstgen %>% factor(labels = c("No", "Yes"))
plot_frq(bns$firstgenplot) + xlab("First Generation Student")
```

The vast majority of respondents (94.7% n = 142) are first generation college students with only 8 (5.3%) not being fist generation students.

### What is your major at CSU, Chico?

```{r}
table(tolower(bns$major)) %>% kable(col.names = c("Major", "Frequency")) %>% kable_styling() %>% scroll_box(width = "500px", height = "500px")
```

### What is your approximate overall Grade Point Average (GPA) for your current degree in progress? `r emo::ji("star")` `r emo::ji("pencil")`

```{r}
plot_frq(bns$SD2) + xlab("GPA")
```

34.0% (n = 51) reported that their GPA is between 2.51 and 3.0, 32.0% (n = 48) reported that their GPA is between 3.01 and 3.5, and 20.0% (n = 30) reported that their GPA is between 2.01 and 2.5. 12.0% (n = 18) reported that their GPA is above 3.5 and lastly 2.0% (n = 3) reported that their GPA is between 1.51 and 2.0.

### How many units (rounded up) are you enrolled in for the current semester at CSU Chico? `r emo::ji("pencil")`

```{r}
bns$units_relevel <- bns$SD3_1
bns$units_relevel[bns$units_relevel < 12] <- "0-11"
bns$units_relevel[bns$units_relevel > 12 & bns$units_relevel <= 15] <- "13-15"
bns$units_relevel[bns$units_relevel >= 16] <- "16+"
plot_frq(bns$units_relevel, ylim = c(0,100)) + xlab("Units Enrolled")
```

53.7% (n = 80) of students filling out this survey are enrolled in 13-15 units in the semester of the survey, a quarter of the students (24.2% n = 36) are enrolled in 12 units, and 20.8% (n = 31) are enrolled in 16 or more units.

### If currently enrolled at more than one college, how many units (rounded up) are you enrolled in for the current semester at other colleges (NOT CSU Chico)?

```{r}
bns$outside_units <- bns$SD4_1
bns$outside_units[bns$outside_units <= 3] <- "1-3"
bns$outside_units[bns$outside_units >= 13] <- "13+"
plot_frq(bns$outside_units, ylim = c(0,5)) + xlab("Units Enrolled Outside CSU Chico")
```

Out of the students who reported they are taking units outside of CSU Chico, about 37.5% (n = 3) are taking 13 or more units in a different college, 25.0% (n = 2) are taking either 1-3 units or 12 units respectively, and only 1 person (12.5%) is enrolled in 10 units outside of CSU Chico.

# Class Standing `r emo::ji("star")`

### Estimate your class level for the 2018-2019 academic school year by units completed (do not include units currently in progress this semester): `r emo::ji("pencil")`

```{r}
plot_frq(bns$SD5) + theme(axis.text.x = element_text(angle = 70, hjust = 1)) + xlab("Class Level")
```

45.0% (n = 67) of respondents reported that they are Juniors (60-89 units), 44.3% (n = 66) reported that they are Seniors (90+ units), 7.4% (n = 11) reported that they are Sophomores (30-59 units), 2.7% (n = 4) reported that they are Freshman (0-29 units), and lastly 0.7% (n = 1) reported that they are a Graduate Student year 2+.

### What month and year did you first attend Chico State? `r emo::ji("pencil")`

Out of all the students who took this survey, the student who attended Chico state the earliest started in `r min(bns$matriculation_date)` and the student who attended the latest started in `r max(bns$matriculation_date)`.

### What month and year do you expect to graduate from Chico State to earn your current degree? `r emo::ji("pencil")`

Out of all the students who took this survey, the student who expects to graduate the earliest expects to graduate in `r min(bns$exp_grad_date, na.rm = TRUE)` and the student who expects to graduate the latest expects to graduate in `r max(bns$exp_grad_date, na.rm = TRUE)`.

### Have you taken a semester off since you began attending Chico State? If so, how many? `r emo::ji("pencil")`

```{r}
plot_frq(bns$SD8_1) + xlab("Semester Taken Off")
```

92.7% (n = 139) of respondents reported that they have not taken a semester off since they began attending Chico State, 2.7% (n = 4) reported that they took 1 semester off, 2.0% (n = 3) reported that they took 2 semesters off, 2.0% (n = 3) reported that they took 3 semesters off, and lastly 0.7% (n = 1) reported that they took 4 semesters off.

# Student Identifiers `r emo::ji("pencil")`

### I receive services through the Accessibility Resource Center or Disability Support Services Center

```{r}
plot_frq(bns$SD9_2) + xlab("Services Through ARC or DSSC")
```

The majority of the students in this survey (87.3% n = 131) report they do not receive services through the
Accessibility Resource Center or Disability Support Services Center and 12.7% (n = 19) report they do.

### I identify as a(an)... `r emo::ji("star")`

* transfer student
* former foster youth/child
* an International student
* non-California resident (Not International)
* Upward Bound,Educational Talent Search,AVID, TRIO, or other college prep program alumni student
* EOP (Educational Opportunity Program) student
* REACH (Raising Educational Achievement in Collaborative Hubs) student
* ESL (English as a Second Language) student
* Veteran of military service
* Active duty military personnel
* student athlete
* DREAM (i.e. undocumented) student
* DACA (i.e. Deferred Action for Childhood Arrivals) student

```{r}
npct <- function(var){
  paste0(sum(var=="Yes", na.rm=TRUE), "/", sum(!is.na(var)), 
         " (", round(mean(var=="Yes", na.rm = TRUE)*100,1), "%)")
}

bns %>% summarise(Transfer = npct(SD9_1), 
                  Foster = npct(SD9_3), 
                  International = npct(SD9_4), 
                  `Non-Resident` = npct(SD9_5), 
                  `College Prep` = npct(SD9_6), 
                  EOP = npct(SD9_7), 
                  REACH = npct(SD9a_1), 
                  ESL = npct(SD9a_2), 
                  Veteran = npct(SD9a_3), 
                  `Active Duty` = npct(SD9a_4), 
                  `Student Athlete` = npct(SD9a_5), 
                  Dreamer = npct(SD9a_6),
                  DACA = npct(SD9a_7)) %>%
  t() %>% kable()

```



