---
title: "Personal Demographics"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
---

```{r, include=FALSE}
source("common_code.R")
```

## Gender `r emo::ji("star")` 

**The US Census lists the following choices for sex: Male Female. Please choose the one that most closely fits your identity.** 

```{r}
plot_frq(bns$D2) + xlab("Sex")
```

Of the 150 participants, 70% of the respondents (n = 105) are Female and 30% of the respondents (n = 45) are Male.

**What was your sex assigned at birth?** 

```{r}
plot_frq(bns$D3, ylim = c(0,130)) + xlab("Sex")
```

Most respondents, or 70.7%, (n = 106) reported that they were Female at birth and 29.3% of the respondents (n = 44) were Male at birth.

**What is your gender identity?** 

```{r}
plot_frq(bns$D4) + xlab("Gender Identity")
```

Most respondents, or 69.3 % of the respondents, identify as a Woman (n = 104), 28.7% identify as a Man (n = 43), and lastly 1.3% (n = 2) identify as Gender Queer or Gender-Nonconforming.

## Race / Ethnicity `r emo::ji("star")`

**How do you identify your race?** 

```{r}
plot_frq(bns$D5, wrap.labels = 10) + xlab("Race")
```

A majority of the respondents did not list their race (48.2% n = 68). 22.0% (n = 31) of the respondents identified as white, followed by 9.9% (n = 14) of the respondents identified as Black or African American. 9.9% (n = 14) of the respondents identified as Mixed race, and 7.8% (n = 11) identified as Asian. Lastly, 1.4% (n = 2) identified as American Indian or Alaska Native, and 0.7% (n = 1) identified as Native Hawaiian or other Pacific Islander.

**How do you identify your ethnicity? **

```{r}
plot_frq(bns$D6, ylim=c(0,130)) + xlab("Ethnicity")
```

Most respondents, or 74.7% (n = 109), identified as Hispanic or Latino and 25.3% (n = 37) identified as Non-Hispanic or Latino.

## Marital Status

**What is your marital status?**

```{r}
plot_frq(bns$D7) + xlab("Marital Status")
```

A large proportion (88.5% n = 131) of the respondents reported that they are single and have never been married. 6.1% (n = 9) reporter they are married, 4.0% (n = 6) reported they are living with a partner, 0.7% (n = 1) reported they are separated, and lastly 0.7% (n = 1) reported they are widowed.

## Citizenship

**Are you a US citizen?**

```{r}
plot_frq(bns$D8) + xlab("Citizenship Status")
```

Most respondents, or 92.6% (n = 137), reported that they are U.S. citizens and 7.4% (n = 11) reported they are not citizens.

**If not a U.S. citizen, are you a lawful permanent resident (i.e. have a “green card”)?**

```{r}
plot_frq(bns$D8a, ylim = c(0,8)) + xlab("Permanent Resident")
```

Out of the participants that were not a U.S. citizen, 54.5% (n = 6) report they are not a permanent resident and 45.5% (n = 5) report they are a permanent resident.

## Dependents

**How many dependents receive more than 50% of their financial support from you?** 

```{r}
bns$dependents_relevel <- bns$D9_1
bns$dependents_relevel[bns$dependents_relevel >= "2"] <- "2+"
plot_frq(bns$dependents_relevel) + xlab("Number of Dependents")
```

Most participants, or 88.0% (n = 132), reported that they have 0 dependents who receive more than 50% of their financial support from them. 6.0% (n = 9) report that they have 1 dependent and 6.0% (n = 9) report that they have 2 or more dependents.

**What is/are the age(s) of your dependent(s)?**

```{r}
a <- bns %>% 
  summarise_at(vars(contains("age_dep_")), sum) %>%
  t() %>% data.frame()
names(a) <- "N"
a$lab <- paste0(a$N, " (", round(a$N/NROW(bns)*100,0), ")%")
a$type <- stringr::str_replace(rownames(a), "age_dep_", "")
a$type <- factor(a$type)
a$type <- a$type %>% fct_relevel(levels = c("lt5", "6_12", "13_18", "19_60", "over61"))
a$type <- factor(a$type, labels = c("0-5", "6-12", "13-18", "19-60", "61+"))
ggplot(a, aes(x=type, y=N)) + geom_col(fill="#336699") +  
        geom_text(aes(label=lab, y=N+.5)) + xlab("Age of Dependents") +
        scale_y_continuous(limits=c(0,10)) + 
        coord_flip()
```

About 5% (n = 8) of the total number of respondents say they have dependents that are between 6-12 years old, 5% (n = 7) say they have dependents that are between 19-60 years old, and only 1 person says they have dependents that are over 61 years old.


## First Generation Student

**Are you a first generation student?** 

```{r}
bns$firstgenplot <- bns$firstgen %>% factor(labels = c("No", "Yes"))
plot_frq(bns$firstgenplot) + xlab("First Generation Student")
```

The vast majority of respondents (94.7% n = 142) are first generation college students with only 8 (5.3%) not being first generation* students.

*First Generation: a student whose parent(s)/legal guardian(s) have not completed a bachelor's degree. 




















