---
title: "Employment"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(ggplot2)
library(sjPlot)
library(kableExtra)
library(knitr)
library(dplyr)
library(tidyverse)

load("../data/bns_clean.Rdata")
bns <- out

opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, cache=FALSE, fig.height=4, fig.width=6, fig.align = 'center')
# don't forget when done with session to turn CACHE = FALSE and clear knitr cache (last option under the knit button)

# Helper functions to display text answers without blank lines
display.text <- function(data, var){
  data %>% filter(!!as.symbol(var)!="") %>% select(!!as.symbol(var)) %>%
           kable(col.names=NULL) %>% 
           kable_styling(full_width = FALSE, 
           bootstrap_options =c("striped", "responsive", "hover", "condensed"))
}

sjPlot::set_theme(base = theme_bw())
```

# Supported Employment `r emo::ji("star")`

### I am approved, awarded, or accepted for work study (with or without a work study job)

```{r}
plot_frq(bns$SD9b_1) + xlab ("Work Study")
```

88.0% (n = 125) of respondents reported that they are approved, awarded, or accepted for work study, and 12.0% (n = 17) are not.

### I participate in CalWorks(i.e. TANF or cash aid for needy families) or Aid to Families with Dependent Children (AFDC)

```{r}
plot_frq(bns$SD9b_2) + xlab("CalWorks/AFDC")
```

76.0% (n = 111) of respondents report that they do not participate in Calworks or Aid to Families with Dependent Children, and 24.0% (n = 35) report they do.

### I participate in the Job Opportunities and Basic Skills (JOBS) Program

```{r}
plot_frq(bns$SD9b_3) + xlab("JOBS Program")
```

95.2% (n = 138) of respondents report that they do not participate in the Job Opportunities and Basic Skills program and 4.8% (n = 7) report they do.

### I participate in the CalFresh Employment or Training (CFET) Program

```{r}
plot_frq(bns$SD9b_4) + xlab("CFET Program")
```

83.3% (n = 120) of respondents report they do not participate in the CalFresh Employment or Training Program and 16.7% (n = 24) report they do not.

### I am enrolled in Workforce Innovation and Opportunity Act (WIOA)

```{r}
plot_frq(bns$SD9b_5) + xlab("WIOA")
```

All respondents in this survey (100% n = 147) report that they are not enrolled in Workforce Innovation and Opportunity Act.

### I am enrolled in Cooperative Agencies Resources for Education (CARE)

```{r}
plot_frq(bns$SD9b_6) + xlab("CARE")
```

A very small percentage (3.4% n = 5) of respondents are enrolled in Cooperative Agencies Resources for Education with the majority (96.6% n = 143) are not.

### I am enrolled in the Mathematics, Engineering, Science achievement (MESA) Program

```{r}
plot_frq(bns$SD9b_7) + xlab("MESA")
```

The majority of respondents (95.3% n = 142) reported that they are not enrolled in the MESA Program while 4.7% (n = 7) report they are.

### I am a student attending CSU, receiving Cal Grant A OR B

```{r}
plot_frq(bns$SD9c_1) + xlab("Cal Grant A or B")
```

87.4% (n = 125) of respondents reported that they do receive either Cal Grant A or B while 12.6% (n = 18) reported they do not.

### I am enrolled in a program that increases employability for current and former foster youth (Guardian Scholars, FYSI, CAFYES, ETV or Extended Foster Care)

```{r}
plot_frq(bns$SD9c_2) + xlab("Foster Youth Program")
```

A large proportion (96.6% n = 144) of respondents reported that they are not enrolled in a program that increases employability for current and former foster youth while 3.4% (n = 5) reported that they are.

### I exert parental control over a dependent household member between the age of 6 and 12 with no adequate childcare

```{r}
plot_frq(bns$SD9c_3) + xlab("Parental Control")
```

All respondents (100% n = 147) reported that they do not exert parental control over a dependent household member between the age of 6 and 12 with no adequate childcare.

### I am a single parent of a dependent household member under the age of 12

```{r}
plot_frq(bns$SD9c_4) + xlab("Single Parent")
```

Only 1 (0.7%) person reported that they are a single parent of a dependent household member under the age of 12 while the rest (99.3% n = 148) reported they are not.

### Which best describes your current housing situation? 

```{r}
test1 <- as.data.frame(table(bns$SD10))
test2 <- as.data.frame(prop.table(table(bns$SD10)))
finaltest <- left_join(test1, test2, by = "Var1")
names(finaltest) <- c("Housing Situation", "n", "%")
finaltest$`%` <- round(finaltest$`%` * 100, 2)
finaltest %>% kable() %>% kable_styling()
```

# Employment `r emo::ji("star")`

### Paid Job or Paid Internship

```{r}
bns$paid_hours <- bns$FSI2
bns$paid_hours[bns$paid_hours >= 1 & bns$paid_hours <= 5] <- "1-5"
bns$paid_hours[bns$paid_hours == 6] <- "6-10"
bns$paid_hours[bns$paid_hours == 7] <- "6-10"
bns$paid_hours[bns$paid_hours == 8] <- "6-10"
bns$paid_hours[bns$paid_hours == 9] <- "6-10"
bns$paid_hours[bns$paid_hours == 10] <- "6-10"
bns$paid_hours[bns$paid_hours > 10 & bns$paid_hours <= 15] <- "11-15"
bns$paid_hours[bns$paid_hours > 15 & bns$paid_hours <= 20] <- "16-20"
bns$paid_hours <- factor(bns$paid_hours, labels = c("0", "1-5", "6-10", "11-15", "16-20", "21"))
```

```{r}
plot_frq(bns$paid_hours) + xlab("Paid Hours")
```

The majority of the students in this survey (n = 51 34.2%) reported that they work 0 paid hours a week, roughly 20% (n = 29) reported they work 6-10 paid hours a week and only 4.7% (n = 7) work 1-5 paid hours a week.

### Unpaid Position or Volunteer

For example, research with faculty on campus, shadowing a professional or volunteering at a shelter.

```{r}
bns$unpaid_hours <- bns$FSI3
bns$unpaid_hours[bns$unpaid_hours >= 1 & bns$unpaid_hours <= 5] <- "1-5"
bns$unpaid_hours[bns$unpaid_hours == 6] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours == 7] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours == 8] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours == 9] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours == 10] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours > 10 & bns$unpaid_hours <= 15] <- "11-15"
bns$unpaid_hours[bns$unpaid_hours > 15 & bns$unpaid_hours <= 20] <- "16-20"
bns$unpaid_hours <- factor(bns$unpaid_hours, labels = c("0", "1-5", "6-10", "11-15", "16-20", "21"))
```

```{r}
plot_frq(bns$unpaid_hours) + xlab("Unpaid Hours")
```

The majority of respondents (n = 87 58.4%) reported that they work 0 unpaid hours a week, 19.5% (n = 29) work 1-5 unpaid hours, and lastly 12.1% (n = 18) reported they work 21 unpaid hours a week.

### If you are currently in a PAID position, what is your average hourly wage from all jobsworked during the academic year?

```{r}
plot_frq(bns$FSI4) + coord_flip() + xlab("Hourly Wage")
```

35.8% (n = 53) of the respondents reported that they make between `$12.00` and `$12.99`/hr and 35.8% (n = 53) reported they are currently not working, while only a total of 6 people reported they make over $14.00 an hour.

### For this survey, household size is determined by the number of people you purchase and prepare food with. This may or may not include your roommate(s). How many people are in your household who purchase and prepare food with you?

```{r}
bns$adj_size <- bns$household_size
bns$adj_size[bns$adj_size >= 5] <- "5+"
plot_frq(bns$adj_size) + xlab("Household Size")
```

63.5% (n = 94) reported that they have 1 other person that they purchase and prepare food with while 16.2% (n = 24) reported that they have 2 other people they purchase and prepare food with. Only 6.8% (n = 10) reported that they have 5 or more other people they purchase and prepare food with.

### How much is your household's gross monthly income (before taxes and not including financial aid)?

```{r}
plot_frq(bns$FSI6) + coord_flip() + xlab("Gross Monthly Income")
```

### Before attending college, did you expect to find or want to find a PAID job or PAID internship during the academic year to help cover your college expenses and personal expenses while in college?

```{r}
plot_frq(bns$FSI7) + xlab("Expected to Find Paid Job")
```

The majority of students (n = 112 83.0%) reported that they did expect to find a paid job during the academic year to help support their expenses while 17.0% (n = 23) did not.

### If you expected or wanted to find a paid job or paid internship, were you successful in securing a position that paid enough to cover your expenses?

```{r}
plot_frq(bns$FSI8) + xlab("Success in Finding Job")
```

34.3% (n = 48) of students reported that they were not able to find a paid position that meets their expenses and 32.1% (n = 45) reported they were sometimes able to find a paid position. 24.3% (n = 34) of students reported that they were able to find a job that almost always has been able to meet their expenses.

## If you have not found paid jobs or internships that have consistently covered your expenses while in college, how strongly do you agree or disagree with these statements?

### I was offered jobs, but did not have transportation to a job or available jobs were not within walking/bike riding/bus distance of my residence or campus.

```{r}
plot_frq(bns$FSI9_1) + xlab("No Transportation")
```

33.6% (n = 37) of respondents reported that they disagree with the statement that they were not able to work because they had no transportation and 17.3% (n = 19) agreed with the statement.

### I searched and applied for jobs but was not offered a job. 

```{r}
plot_frq(bns$FSI9_2) + xlab("Not Offered a Job")
```

31.8% (n = 35) of respondents agreed that they searched for a job but was never offered a job and 16.4% (n = 18) reported they disagree with the statement.

### I searched for jobs, but my class schedule or study time was not compatible with any jobs that were offered to me.

```{r}
plot_frq(bns$FSI9_3) + xlab("Schedule Conflict")
```

42.7% (n = 47) of respondents agreed that their class or study schedule conflicted with the work hours so were not able to work and 15.4% (n = 17) reported that they disagree with the statement.

### I searched for jobs, but family obligations interfered with any jobs offered to me.

```{r}
plot_frq(bns$FSI9_4) + xlab("Family Obligations Interfered")
```

36.4% (n = 40) of respondents disagreed that their family obligations interfered with any jobs offered to them and 10.9% (n = 12) agreed with the statement.

### I expected to find a job, but never searched for a job because my school work (studying) did not allow time for a job.

```{r}
plot_frq(bns$FSI9_5) + xlab("No Time")
```

25.4% (n = 28) disagreed with 

### I expected to find a job, but never searched for a job, due to other unexpected obligations or conflicts that did not allow time for a job.

```{r}
plot_frq(bns$FSI9_6) + xlab("Unexpected Obligations")
```

### I did not expect to or want to find a job while in college.

```{r}
plot_frq(bns$FSI9_7) + xlab("Did Not Expect a Job")
```




