---
title: "Employment"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(ggplot2)
library(sjPlot)
library(kableExtra)
library(knitr)
library(dplyr)
library(tidyverse)

load("../data/bns_clean.Rdata")
bns <- out

opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, cache=FALSE, fig.height=4, fig.width=6, fig.align = 'center')
# don't forget when done with sessino to turn CACHE = FALSE and clear knitr cache (last option under the knit button)

# Helper functions to display text answers without blank lines
display.text <- function(data, var){
  data %>% filter(!!as.symbol(var)!="") %>% select(!!as.symbol(var)) %>%
           kable(col.names=NULL) %>% 
           kable_styling(full_width = FALSE, 
           bootstrap_options =c("striped", "responsive", "hover", "condensed"))
}

sjPlot::set_theme(base = theme_bw())
```

# Supported Employment `r emo::ji("star")`

### I am approved, awarded, or accepted for work study (with or without a work study job)

```{r}
plot_frq(bns$SD9b_1) + xlab ("Work Study")
```

88.0% (n = 125) of respondents reported that they are approved, awarded, or accepted for work study, and 12.0% (n = 17) are not.

### I participate in CalWorks(i.e. TANF or cash aid for needy families) or Aid to Families with Dependent Children (AFDC)

```{r}
plot_frq(bns$SD9b_2) + xlab("CalWorks/AFDC")
```

76.0% (n = 111) of respondents report that they do not participate in Calworks or Aid to Families with Dependent Children, and 24.0% (n = 35) report they do.

### I participate in the Job Opportunities and Basic Skills (JOBS) Program

```{r}
plot_frq(bns$SD9b_3) + xlab("JOBS Program")
```

95.2% (n = 138) of respondents report that they do not participate in the Job Opportunities and Basic Skills program and 4.8% (n = 7) report they do.

### I participate in the CalFresh Employment or Training (CFET) Program

```{r}
plot_frq(bns$SD9b_4) + xlab("CFET Program")
```

83.3% (n = 120) of respondents report they do not participate in the CalFresh Employment or Training Program and 16.7% (n = 24) report they do not.

### I am enrolled in Workforce Innovation and Opportunity Act (WIOA)

```{r}
plot_frq(bns$SD9b_5) + xlab("WIOA")
```

All respondents in this survey (100% n = 147) report that they are not enrolled in Workforce Innovation and Opportunity Act.

### I am enrolled in Cooperative Agencies Resources for Education (CARE)

```{r}
plot_frq(bns$SD9b_6) + xlab("CARE")
```

A very small percentage (3.4% n = 5) of respondents are enrolled in Cooperative Agencies Resources for Education with the majority (96.6% n = 143) are not.

### I am enrolled in the Mathematics, Engineering, Science achievement (MESA) Program

```{r}
plot_frq(bns$SD9b_7) + xlab("MESA")
```

The majority of respondents (95.3% n = 142) reported that they are not enrolled in the MESA Program while 4.7% (n = 7) report they are.

### I am a student attending CSU, receiving Cal Grant A OR B

```{r}
plot_frq(bns$SD9c_1) + xlab("Cal Grant A or B")
```

87.4% (n = 125) of respondents reported that they do receive either Cal Grant A or B while 12.6% (n = 18) reported they do not.

### I am enrolled in a program that increases employability for current and former foster youth (Guardian Scholars, FYSI, CAFYES, ETV or Extended Foster Care)

```{r}
plot_frq(bns$SD9c_2) + xlab("Foster Youth Program")
```

A large proportion (96.6% n = 144) of respondents reported that they are not enrolled in a program that increases employability for current and former foster youth while 3.4% (n = 5) reported that they are.

### I exert parental control over a dependent household member between the age of 6 and 12 with no adequate childcare

```{r}
plot_frq(bns$SD9c_3) + xlab("Parental Control")
```

All respondents (100% n = 147) reported that they do not exert parental control over a dependent household member between the age of 6 and 12 with no adequate childcare.

### I am a single parent of a dependent household member under the age of 12

```{r}
plot_frq(bns$SD9c_4) + xlab("Single Parent")
```

Only 1 (0.7%) person reported that they are a single parent of a dependent household member under the age of 12 while the rest (99.3% n = 148) reported they are not.

### Which best describes your current housing situation? 

```{r}
test1 <- as.data.frame(table(bns$SD10))
test2 <- as.data.frame(prop.table(table(bns$SD10)))
finaltest <- left_join(test1, test2, by = "Var1")
names(finaltest) <- c("Housing Situation", "n", "%")
finaltest$`%` <- round(finaltest$`%` * 100, 2)
finaltest %>% kable() %>% kable_styling()
```

# Employment `r emo::ji("star")`




