---
title: "Financial Support and Income"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
---

```{r, include=FALSE}
source("common_code.R")
```

# Financial Aid

**Select ALL sources of financial support you currently receive while attending college? (Mark all that apply)**

```{r}
finaid <- bns %>% select(FS_PellGrant,
                         FS_CalGrantAorB,
                         FS_NonAtheletic,
                         FS_Atheletic,
                         FS_OtherGrants,
                         FS_FedLoans,
                         FS_PrivateLoans,
                         FS_WorkStudy,
                         FS_GIBill,
                         FS_Other)

names(finaid) <- c("Pell Grant",
                   "Cal Grant A or B",
                   "Non Athletic",
                   "Athletic",
                   "Other Grants",
                   "Federal Loans",
                   "Private Loans",
                   "Work-study",
                   "GI Bill",
                   "Other")
```

```{r}
multi.table(finaid) %>% kable(col.names = c("n", "%")) %>% kable_styling()
```

# Hourly Wages

**If you are currently in a PAID position, what is your average hourly wage from all jobs worked during the academic year?**

```{r}
plot_frq(bns$FSI4, vjust="center", hjust="left") + coord_flip() + xlab("Hourly Wage")
```

35.8% (n = 53) of the respondents reported that they make between `$12.00` and `$12.99`/hr and 35.8% (n = 53) reported they are currently not working, while only a total of 6 people reported they make over $14.00 an hour.

# Receive SSI

**Do you receive Supplemental Security Income (SSI) in California?**

```{r}
plot_frq(bns$FSI10) + xlab("Supplemental Security Income")
```

The majority of respondents (96.3% n = 131) reported that they do not receive Supplemental Security Income in California and 3.7% (n = 5) reported they do.













