---
title: "Health"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(ggplot2)
library(sjPlot)
library(kableExtra)
library(knitr)
library(dplyr)
library(tidyverse)
library(questionr)

load("../data/bns_clean.Rdata")
bns <- out

opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, cache=FALSE, fig.height=4, fig.width=6, fig.align = 'center')
# don't forget when done with sessino to turn CACHE = FALSE and clear knitr cache (last option under the knit button)

# Helper functions to display text answers without blank lines
display.text <- function(data, var){
  data %>% filter(!!as.symbol(var)!="") %>% select(!!as.symbol(var)) %>%
           kable(col.names=NULL) %>% 
           kable_styling(full_width = FALSE, 
           bootstrap_options =c("striped", "responsive", "hover", "condensed"))
}

sjPlot::set_theme(base = theme_bw())
```

# Physical Activity

## On how many of the past 7 days did you

### Do moderate-intensity cardio or aerobic exercise (caused a noticeable increase in heart rate, such as brisk walk) for at least 30 minutes?

```{r}
plot_frq(bns$PA1_1) + xlab("# of Days/Week")
```

25.0% (n = 37) of respondents reported that they do not do any days a week of cardio or aerobic excercise for at least 30 minutes, 11.5% (n = 17) reported that they exercise for 1 day, and 18.9% (n = 28) reported that they excerise for 2 days.

### Do vigorous-intensity cardio or aerobic exercise (caused large increases in breathing or heart rate, such as jogging) for at least 20 minutes?

```{r}
plot_frq(bns$PA1_2) + xlab("# of Days/Week") + ylim(c(0,70))
```

36.5% (n = 54) of respondents reported that they did not do vigorous-intensity cardio for at least 20 minutes per day in the past 7 days, 18.2% (n = 27) reported they did for 1 day, and 20.9% (n = 31) reported they did for 2 days.

### Do vigorous-intensity cardio or aerobic exercise (caused large increases in breathing or heart rate, such as jogging) for at least 20 minutes?

```{r}
plot_frq(bns$PA1_3) + xlab("# of Days") + ylim(c(0,90))
```

47.3% (n = 70) of respondents that they did not do 8-10 strength training exercises per day in the past 7 days, 11.5% (n = 17) reported they did for 1 day, and 16.2% (n = 24) reported they did for 2 days.

# Smoking

## Have you smoked at least 100 tobacco cigarettes in your entire life? 

```{r}
plot_frq(bns$TU1) + xlab("100 Cigarettes in Entire Life") + ylim(c(0,180))
```

Only 7.4% (n = 11) of respondents reported that they have smoked over 100 cigarettes in their entire life and 92.6% (n = 137) reported they have not.

## How frequently do you currently smoke tobacco cigarettes?

```{r}
plot_frq(bns$TU2) + xlab("Frequency of Smoking Cigarettes")
```

3.4% (n = 5) reported that they smoke cigarettes on some days and 96.6% (n = 142) reported that they do not smoke cigarettes.

# Sleep

## On average, during the academic year, how many hours of sleep do you get in a typical 24-hour period during the week?

```{r}
nsleep <- as.data.frame(table(bns$SLPD1_1))
pctsleep <- as.data.frame(prop.table(table(bns$SLPD1_1)))
sleep <- left_join(nsleep,pctsleep, by = "Var1")
names(sleep) <- c("Hours", "n", "%")
sleep$`%` <- round(sleep$`%` * 100, 2)
sleep %>% kable() %>% kable_styling()
```

## On average, during the academic year, howmany hours of sleep do you getin a typical 24-hour period during weekends?

```{r}
nsleep2 <- as.data.frame(table(bns$SLPD2_1))
pctsleep2 <- as.data.frame(prop.table(table(bns$SLPD2_1)))
sleep2 <- left_join(nsleep2,pctsleep2, by = "Var1")
names(sleep2) <- c("Hours", "n", "%")
sleep2$`%` <- round(sleep2$`%` * 100, 2)
sleep2 %>% kable() %>% kable_styling()
```

## On average, how many times per month do you feel deprived of sleep?

```{r}
nsleep3 <- as.data.frame(table(bns$SLPD3_1))
pctsleep3 <- as.data.frame(prop.table(table(bns$SLPD3_1)))
sleep3 <- left_join(nsleep3,pctsleep3, by = "Var1")
names(sleep3) <- c("Days", "n", "%")
sleep3$`%` <- round(sleep3$`%` * 100, 2)
sleep3 %>% kable() %>% kable_styling()
```

# Select the activities that cause you to feel deprived of sleep

```{r}
sleep_act <- bns %>% select(starts_with("SLPD4_")) %>% select(-c("SLPD4_6_TEXT"))
names(sleep_act) <- c("Studying or finishing coursework",
                      "Working a paid, or unpaid job or internship",
                      "Attending social activities or events",
                      "Spending time with family or friends",
                      "Watching movies, playing games, social media etc.",
                      "Other")
```

```{r}
multi.table(sleep_act) %>% kable(col.names = c("n", "%")) %>% kable_styling()
```

## How frequently do you feel tired while at work or school?

```{r}
plot_frq(bns$SLPD5) + xlab("Frequency of Feeling Tired")
```

## Have you fallen asleep in class in the past 12 months?

```{r}
plot_frq(bns$SLPD6) + xlab("Fallen Asleep in Class")
```

## How many days in the past month have you experienced heightened anxiety, stress, depression and/or problems with emotions?

```{r}
bns$MH1_1[bns$MH1_1 >= 15 & bns$MH1_1 < 30] <- "15-29"
bns$MH1_1[bns$MH1_1 >= 30] <- "30+"
plot_frq(bns$MH1_1) + xlab("# of Days")
```

## Have you received or tried to receive mental health services over the past 12months?

```{r}
plot_frq(bns$MH2) + xlab("Received Mental Health Services") + ylim(c(0,100))
```



# Food & Nutrtion 
## “In the last 12 months, the food that (I/we) bought just didn’t last, and (I/we) didn’t have money to get more.” Was that often, sometimes,or nevertrue for (you/your household)?

```{r}
plot_frq(bns$HH3) + xlab("Food Didn't Last + No Money to Get More")
```

## “In the last 12 months, (I/we) couldn’t afford to eat balanced meals.” Was that often, sometimes, or never true for (you/your household)?

```{r}
plot_frq(bns$HH4) + xlab("Couldn't Afford Balanced Meals")
```

## In the last 12 months, did you or other adults in your household,ever cut the size of your meals or skip meals because there wasn’t enough money for food?

```{r}
plot_frq(bns$AD1) + xlab("Cut Size/Skip Meals Because No Money")
```

## How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?

```{r}
plot_frq(bns$AD1a) + xlab("Cut Size/Skip Meals Because No Money")
```

## In the last 12 months, did you ever eat less than you felt you should because there was not enough money for food?

```{r}
plot_frq(bns$AD2) + xlab("Ate Less Because Not Enough Money")
```

## How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?

```{r}
plot_frq(bns$AD2a) + xlab("Ate Less Because Not Enough Money")
```

## In the last 12 months, were you ever hungry but you did not eat because there wasn’t enough money for food?

```{r}
plot_frq(bns$AD3) + xlab("Hungry Because Not Eating Due to Money")
```

## How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?

```{r}
plot_frq(bns$AD3a) + xlab("Hungry Because Not Eating Due to Money")
```

## In the last 12 months, did you lose weight because there wasn’t enough money for food?

```{r}
plot_frq(bns$AD4) + xlab("Lose Weight Because No Money for Food")
```

## In the last 12 months, did (you/you or other adults in your household) ever not eat for a whole day because there wasn’t enough money for food? 

```{r}
plot_frq(bns$AD5) + xlab("Adults did not Eat Because No Money")
```

## How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?

```{r}
plot_frq(bns$AD5a) + xlab("Adults did not Eat Because No Money") + ylim(c(0,20))
```

## Food Insecure

```{r}
bns$food_insecurity <- factor(bns$food_insecurity, labels = c("No", "Yes"))
plot_frq(bns$food_insecurity) + xlab("Food Insecure")
```









