---
title: "Health"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
---

```{r, include=FALSE}
source("common_code.R")
```


# Physical Activity

## On how many of the past 7 days did you:

**Do moderate-intensity cardio or aerobic exercise (caused a noticeable increase in heart rate, such as brisk walk) for at least 30 minutes?**

```{r}
plot_frq(bns$PA1_1) + xlab("# of Days/Week")
```

One fourth, or 25.0% (n = 37) of respondents, reported that they do not do any days a week of cardio or aerobic exercise for at least 30 minutes, 11.5% (n = 17) reported that they exercise for 1 day, and 18.9% (n = 28) reported that they exercise for 2 days.

**Do vigorous-intensity cardio or aerobic exercise (caused large increases in breathing or heart rate, such as jogging) for at least 20 minutes?**

```{r}
plot_frq(bns$PA1_2) + xlab("# of Days/Week") + ylim(c(0,70))
```

36.5% (n = 54) of respondents reported that they did not do vigorous-intensity cardio for at least 20 minutes per day in the past 7 days, 18.2% (n = 27) reported they did for 1 day, and 20.9% (n = 31) reported they did for 2 days.

**Do vigorous-intensity cardio or aerobic exercise (caused large increases in breathing or heart rate, such as jogging) for at least 20 minutes?**

```{r}
plot_frq(bns$PA1_3) + xlab("# of Days") + ylim(c(0,90))
```

Almost half, or 47.3% (n = 70) of respondents, that they did not do 8-10 strength training exercises per day in the past 7 days, 11.5% (n = 17) reported they did for 1 day, and 16.2% (n = 24) reported they did for 2 days.

# Smoking

**Have you smoked at least 100 tobacco cigarettes in your entire life?** 

```{r}
plot_frq(bns$TU1) + xlab("100 Cigarettes in Entire Life") + ylim(c(0,180))
```

Only 7.4% (n = 11) of respondents reported that they have smoked over 100 cigarettes in their entire life and 92.6% (n = 137) reported they have not.

**How frequently do you currently smoke tobacco cigarettes?**

```{r}
plot_frq(bns$TU2) + xlab("Frequency of Smoking Cigarettes")
```

Only 3.4% (n = 5) respondents reported that they smoke cigarettes on some days and 96.6% (n = 142) reported that they do not smoke cigarettes.

# Sleep

**On average, during the academic year, how many hours of sleep do you get in a typical 24-hour period during the week?**


```{r}
plot_frq(bns$SLPD1_1, type = c("histogram")) + xlab("Average Hours of Sleep During Academic Year")
```


The majority of respondents, or 75.68%, reported getting an average of 5-7 hours of sleep in a typical 24-hour period during the academic year. 

**On average, during the academic year, how many hours of sleep do you get in a typical 24-hour period during weekends?**


```{r}
plot_frq(bns$SLPD2_1, type = c("histogram")) + xlab("Average Hours of Sleep During Weekends")
```
The majority of respondents, or 79.06%, reported getting an average of 6-10 hours of sleep in a typical 24-hour period during the weekends. 

**On average, how many times per month do you feel deprived of sleep?**


```{r}
plot_frq(bns$SLPD3_1, type = c("histogram")) + xlab("Average Times Felt Deprived of Sleep Per Month")
```


**Select the activities that cause you to feel deprived of sleep**

```{r}
sleep_act <- bns %>% select(starts_with("SLPD4_")) %>% select(-c("SLPD4_6_TEXT"))
names(sleep_act) <- c("Studying or finishing coursework",
                      "Working a paid, or unpaid job or internship",
                      "Attending social activities or events",
                      "Spending time with family or friends",
                      "Watching movies, playing games, social media etc.",
                      "Other")
```

```{r}
multi.table(sleep_act) %>% kable(col.names = c("n", "%")) %>% kable_styling()
```

The majority of respondents, or 94.7%, reported that the activity of studying or finishing coursework caused them to feel deprived of sleep.

**How frequently do you feel tired while at work or school?**

```{r}
plot_frq(bns$SLPD5) + xlab("Frequency of Feeling Tired")
```

Most respondents, or 55.4%, reported occasionally feeling tired while at work or school, while 35% reported always feeling tired at work or school. 

**Have you fallen asleep in class in the past 12 months?**

```{r}
plot_frq(bns$SLPD6) + xlab("Fallen Asleep in Class")
```

More than half of respondents, or 57.1%, reported they had not fallen asleep in class in the past 12 months. 

## Stress, Anxiety, & Depression

**How many days in the past month have you experienced heightened anxiety, stress, depression and/or problems with emotions?**


```{r}
bns$MH1_1[bns$MH1_1 >= 15 & bns$MH1_1 < 30] <- "15-29"
bns$MH1_1[bns$MH1_1 >= 30] <- "30+"

plot_frq(bns$MH1_1) + xlab("# of Days") + ylab("Count")
```

**By Gender Identity**

All but three respondents selected either Male or Female for their gender identity. Their response distribution is below. 

```{r, fig.width=12, fig.height=5}
toplot <- bns %>% filter(D4 %in% c('Man', 'Woman'))
plot_xtab(x=toplot$MH1_1, grp=toplot$D4, margin="col", show.total = FALSE) + 
          xlab("# of Days") + ylab("Percent (count)") + 
          theme(legend.position="top", legend.title=element_blank()) 

```

```{r, eval=FALSE}
bns$MH1_1[bns$D4=="Gender Queer or Gender-Nonconforming"]
bns$MH1_1[bns$D4=="Gender unlisted:"]
```

* Two respondents selected `Gender Queer or Gender-Nonconforming`, one reported `15-29` days, the other `30+` days. 
* The one respondent who selected `Gender Unlisted` reported `10` days. 

## Mental Health Services

**Have you received or tried to receive mental health services over the past 12months?**

```{r}
plot_frq(bns$MH2) + xlab("Received Mental Health Services") + ylim(c(0,100))
```

Over half of the respondents, or 58.9%, answered no when asked if they had received, or tried to receive, mental health services over the past 12 months. 


# Food Security 

## Food/Meal Habits in the Last 12 Months

**“In the last 12 months, the food that (I/we) bought just didn’t last, and (I/we) didn’t have money to get more.” Was that often, sometimes, or never true for (you/your household)?**

```{r}
plot_frq(bns$HH3) + xlab("Food Didn't Last + No Money to Get More")
```

Over half of respondents, or 54.3%, said it is sometimes true that in the last 12 months, the food that was bought didn't last and they didn't have money to get more. 21.4% of respondents said that was often true. 

**“In the last 12 months, (I/we) couldn’t afford to eat balanced meals.” Was that often, sometimes, or never true for (you/your household)?**

```{r}
plot_frq(bns$HH4) + xlab("Couldn't Afford Balanced Meals")
```

Over half of respondents, or 52.1%, said it is sometimes true that in the last 12 months, they couldn't afford to eat balanced meals. 23.2% of respondents said that was often true. 

**In the last 12 months, did you or other adults in your household, ever cut the size of your meals or skip meals because there wasn’t enough money for food?**

```{r}
plot_frq(bns$AD1) + xlab("Cut Size/Skip Meals Because No Money")
```

Over half of respondents, or 58%, reported that they, or the other adults in their household, cut the size of their meals, or skipped meals, because there was not enough money for food. 

**How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?**

```{r}
plot_frq(bns$AD1a) + xlab("Cut Size/Skip Meals Because No Money")
```

Of the respondents that answered yes to cutting the size of their meals, or skipping meals, over half (54.5%) said this happened some months but not every month. 27.3% reported this happened almost every month. 

**In the last 12 months, did you ever eat less than you felt you should because there was not enough money for food?**

```{r}
plot_frq(bns$AD2) + xlab("Ate Less Because Not Enough Money")
```

The majority of respondents, or 61.8%, reported eating less then they felt they should over the last 12 months because there was not enough money for food. 

**How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?**

```{r}
plot_frq(bns$AD2a) + xlab("Ate Less Because Not Enough Money")
```

Of those that responded yes that they ate less because there was not enough money for food, about half (50.6%) reported this happened some months but not every month. 24.7% of respondents reported this happened almost every month. 

**In the last 12 months, were you ever hungry but you did not eat because there wasn’t enough money for food?**

```{r}
plot_frq(bns$AD3) + xlab("Hungry Because Not Eating Due to Money")
```

Over half of respondents, or 54.5%, reported that there were times they were hungry but did not eat because there wasn't enough money for food. 

**How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?**

```{r}
plot_frq(bns$AD3a) + xlab("Hungry Because Not Eating Due to Money")
```

Of those that responded yes they were hungry but did not eat because lack of money for food, more than half, or 55.3%, reported this happened some months but not every month. 22.4% of respondents reported this happened almost every month.

**In the last 12 months, did you lose weight because there wasn’t enough money for food?**

```{r}
plot_frq(bns$AD4) + xlab("Lose Weight Because No Money for Food")
```
Most respondents (67.4%) reported they did not lose weight because there wasn't enough money for food. 
 
**In the last 12 months, did (you/you or other adults in your household) ever not eat for a whole day because there wasn’t enough money for food?** 

```{r}
plot_frq(bns$AD5) + xlab("Adults did not Eat Because No Money")
```

Most respondents (74.8%) reported that none of the adults in their household ever went a whole day without eating because there wasn't enough money for food. 

**How often did this happen—almost every month, some months but not every month, or in only 1 or 2 months?**

```{r}
plot_frq(bns$AD5a) + xlab("Adults did not Eat Because No Money") + ylim(c(0,20))
```

Out of the 34 respondents that answered yes, either they or their adult household member went a whole day without eating because there wasn't enough money for food, over half (51.6%) reported this happened some months but not every month. 22.6% reported this happened every month.  

## Food Insecure

```{r}
bns$food_insecurity <- factor(bns$food_insecurity, labels = c("No", "Yes"))
plot_frq(bns$food_insecurity) + xlab("Food Insecure")
```

The majority of respondents, or 65.3%, reported that yes, they were food insecure. 34.7% reported that no, they were not food insecure. 

## Campus Meal Plans

**Does anyone in your household get more than half (11 or more) of their meals per week from another source (e.g. university meal plan)?** 

```{r}
plot_frq(bns$FSI11) + xlab("More than Half Meals from Another Source")
```

The majority of respondents (97.0% n = 129) reported that they do not have any people in their household that have more than half of their meals from another source and 3.0% (n = 4) reported they do.







