---
title: "Health"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
---

```{r, include=FALSE}
source("common_code.R")
```

# Physical Activity

## On how many of the past 7 days did you:

**Do moderate-intensity cardio or aerobic exercise (caused a noticeable increase in heart rate, such as brisk walk) for at least 30 minutes?**

```{r}
plot_frq(bns$PA1_1) + xlab("# of Days/Week")
```

One fourth, or 25.0% (n = 37) of respondents, reported that they do not do any days a week of cardio or aerobic exercise for at least 30 minutes, 11.5% (n = 17) reported that they exercise for 1 day, and 18.9% (n = 28) reported that they exercise for 2 days.

**Do vigorous-intensity cardio or aerobic exercise (caused large increases in breathing or heart rate, such as jogging) for at least 20 minutes?**

```{r}
plot_frq(bns$PA1_2) + xlab("# of Days/Week") + ylim(c(0,70))
```

36.5% (n = 54) of respondents reported that they did not do vigorous-intensity cardio for at least 20 minutes per day in the past 7 days, 18.2% (n = 27) reported they did for 1 day, and 20.9% (n = 31) reported they did for 2 days.

**Do vigorous-intensity cardio or aerobic exercise (caused large increases in breathing or heart rate, such as jogging) for at least 20 minutes?**

```{r}
plot_frq(bns$PA1_3) + xlab("# of Days") + ylim(c(0,90))
```

Almost half, or 47.3% (n = 70) of respondents, that they did not do 8-10 strength training exercises per day in the past 7 days, 11.5% (n = 17) reported they did for 1 day, and 16.2% (n = 24) reported they did for 2 days.

# Tobacco Use

**Have you smoked at least 100 tobacco cigarettes in your entire life?** 

```{r}
plot_frq(bns$TU1) + xlab("100 Cigarettes in Entire Life") + ylim(c(0,180))
```

Only 7.4% (n = 11) of respondents reported that they have smoked over 100 cigarettes in their entire life and 92.6% (n = 137) reported they have not.

**How frequently do you currently smoke tobacco cigarettes?**

```{r}
plot_frq(bns$TU2) + xlab("Frequency of Smoking Cigarettes")
```

Only 3.4% (n = 5) respondents reported that they smoke cigarettes on some days and 96.6% (n = 142) reported that they do not smoke cigarettes.

# Sleep

**On average, during the academic year, how many hours of sleep do you get in a typical 24-hour period during the week?**


```{r}
plot_frq(bns$SLPD1_1, type = c("histogram")) + xlab("Average Hours of Sleep During Academic Year")
```


The majority of respondents, or 75.68%, reported getting an average of 5-7 hours of sleep in a typical 24-hour period during the academic year. 

**On average, during the academic year, how many hours of sleep do you get in a typical 24-hour period during weekends?**


```{r}
plot_frq(bns$SLPD2_1, type = c("histogram")) + xlab("Average Hours of Sleep During Weekends")
```
The majority of respondents, or 79.06%, reported getting an average of 6-10 hours of sleep in a typical 24-hour period during the weekends. 

**On average, how many times per month do you feel deprived of sleep?**


```{r}
plot_frq(bns$SLPD3_1, type = c("histogram")) + xlab("Average Times Felt Deprived of Sleep Per Month")
```


**Select the activities that cause you to feel deprived of sleep**

```{r}
sleep_act <- bns %>% select(starts_with("SLPD4_")) %>% select(-c("SLPD4_6_TEXT"))
names(sleep_act) <- c("Studying or finishing coursework",
                      "Working a paid, or unpaid job or internship",
                      "Attending social activities or events",
                      "Spending time with family or friends",
                      "Watching movies, playing games, social media etc.",
                      "Other")
```

```{r}
multi.table(sleep_act) %>% kable(col.names = c("n", "%")) %>% kable_styling()
```

The majority of respondents, or 94.7%, reported that the activity of studying or finishing coursework caused them to feel deprived of sleep.

**How frequently do you feel tired while at work or school?**

```{r}
plot_frq(bns$SLPD5) + xlab("Frequency of Feeling Tired")
```

Most respondents, or 55.4%, reported occasionally feeling tired while at work or school, while 35% reported always feeling tired at work or school. 

**Have you fallen asleep in class in the past 12 months?**

```{r}
plot_frq(bns$SLPD6) + xlab("Fallen Asleep in Class")
```

More than half of respondents, or 57.1%, reported they had not fallen asleep in class in the past 12 months. 

# Eating and Cooking Habits

**For each of the following statements, indicate how strongly agree or disagree about your current eating and cooking habits**

```{r, fig.width=8}
eh1 <- bns %>% select(starts_with("EH1_"))
names(eh1) <- c("No Access to a Kitchen",
                  "Secure Place to Store Food",
                  "No Room to Store Food",
                  "Thinking about Food is Stressful",
                  "Wish I Had more Food to Eat",
                  "Always Skip Meals",
                  "Don't Cook or Shop for Food",
                  "No One Cooks at Home",
                  "Do Not Think about Habits")
plot_likert(eh1, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

## How many servings of fruits and vegetables do you usually consume per day? 

```{r}
plot_frq(bns$EH2) + xlab("Servings of Fruit and Vegetables")
```

The majority of respondents (n = 101 70.6%) reported that they consume 1-2 servings of fruit and vegetables a day and 16.1% (n = 23) reported that they consume none.

## Drinks (juice, water, alcohol, etc.)

**How many ounces of 100% fruit juices like orange juice, apple juice or grape juice do you consume each day?** 

```{r}
plot_frq(bns$EH3) + xlab("Ounces of 100% Fruit Juice")
```

More than half, or 52.4% (n = 76) of respondents, reported that they drink no 100% fruit juice each day and 34.5% (n = 50) reported that they drink between 1 to 8 ounces a day.

**How many ounces of regular soda, cola, or pop, sports drink, or energy drinks do you consume each day?** 

```{r}
plot_frq(bns$EH4, ylim = c(0,85)) + xlab("Ounces of Soda")
```

Almost half, or 48.6% (n = 71) of respondents, reported that they don't drink any soda each day and 24.0% (n = 35) reported they drink between 1 to 8 ounces a day.

**How many ounces or cups of water or unsweetened clear drinks, such as tea, do you consume each day?** 

```{r}
bns$EH5[bns$EH5 == "24-36 ounces"] <- "25-36 ounces"
bns$EH5_f <- factor(bns$EH5, levels = c("Zero", "1-8 ounces", "9-16 ounces",
                                        "17-24 ounces", "25-36 ounces",
                                        "37-48 ounces", "49-56 ounces",
                                        "57-64 ounces", "65 ounces or more"))
```

```{r}
plot_frq(bns$EH5_f,vjust = "center", y.offset = 3) + xlab("Ounces of Unsweetened Drinks") + coord_flip() + ylim(c(0,40))
```

About 19.0% (n = 27) of respondents reported that they drink 1-8 ounces of water or other unsweetened drinks a day, 7.0% (n = 10) reported they do not drink any ounces of unsweetened drinks a day, and 9.2% (n = 13) reported that they drink more than 65 ounces a day.

**How often do you consume at least one serving of alcohol?** 

```{r}
plot_frq(bns$EH8) + xlab("Alcohol Consumption")
```

Half, or 50.0% (n = 73) of respondents, reported that they do not drink alcohol in a week and 43.1% (n = 63) reported they drink at least one serving of alcohol between 1 to 2 days a week.

**Typically, how many servings of alcohol do you consume when you drink alcohol?** 

```{r}
plot_frq(bns$EH8a, ylim = c(0,45)) + xlab("Servings of Alcohol")
```

More than half, or 54.7% (n = 35) of respondents, reported that when they consume alcohol, they consume between 1 to 2 servings and 26.6% (n = 17) reported that when they consume alcohol, they consume between 3 to 4 servings.


## Dining Out or Meal Replacements

**How frequently do you eat out at family-style or sit-down restaurants/café types of dining establishment per week?** 

```{r}
plot_frq(bns$EH6) + xlab("# of Time Dining Out")
```

38.9% (n = 56) of respondents reported that they do not go out to sit-down restaurants in a week and 45.8% (n = 66) reported that they go out between 1 to 2 times in a week.

**How frequently do you eat from fast food restaurants, convenience stores, or vending machines for a meal or meal replacement?** 

```{r}
plot_frq(bns$EH7) + xlab("# of Time Eating Fast Food")
```

20.5% (n = 30) of respondents reported that they do not eat fast food, from convenience stores, or vending machines in a week and 47.3% (n = 69) reported that they eat fast food between 1 to 2 times a week.

## The following questions pertain to how comfortable you feel about buying or preparing food

```{r, fig.width=8}
eh9 <- bns %>% select(starts_with("EH9_"))
names(eh9) <- c("Use Same Healthy Ingredient in More Than One Meal",
                "Basic Cooking Skills",
                "Buy Healthy Foods on a Budget",
                "Cook Healthy Foods on a Budget")
plot_likert(eh9, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```









## Campus Meal Plans

**Does anyone in your household get more than half (11 or more) of their meals per week from another source (e.g. university meal plan)?** 

```{r}
plot_frq(bns$FSI11) + xlab("More than Half Meals from Another Source")
```

The majority of respondents (97.0% n = 129) reported that they do not have any people in their household that have more than half of their meals from another source and 3.0% (n = 4) reported they do.

