---
title: "Food Pantry"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
---

```{r, include=FALSE}
source("common_code.R")
sjPlot::set_theme(base = theme_bw())
```


# Impact of Pantries

**For the following questions, please choose how much you agree or disagree with the impact campus food pantries/food banks has or had on your life.**

**While I utilize/utilized campus food pantry/pantries or local food bank(s):**

```{r, fig.width=8, fig.height=8}
src2a <- bns %>% select(starts_with("SRC2a_"))
names(src2a) <- c("Worked Fewer Paid Hours",
                  "More Time for Unpaid Hours",
                  "More Money for Bills",
                  "More Money for Entertainment",
                  "Shop More at Farmers' Market",
                  "Learned More about Healthy Foods",
                  "Purchase More Healthy Foods",
                  "Cook More at Home",
                  "Consumed a Healthier Diet",
                  "Consumed Less Fast Food",
                  "Consumed Fewer Processed Foods",
                  "Consumed Fewer Sweetened Beverages",
                  "Consumed Fewer Alcoholic Beverages")
plot_likert(src2a, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

**While I utilize/utilized campus food pantry/pantries or local food bank(s):** 

```{r, fig.width=8, fig.height=8}
src2b <- bns %>% select(starts_with("SRC2b_"))
names(src2b) <- c("Enrolled in More Classes",
                  "Concentrated More in Classes",
                  "Grades have Improved",
                  "More Time to Study for Exams",
                  "More Time to Prepare for Class",
                  "More Time for Homework",
                  "More Time for Office Hours",
                  "More Time to Attend All Classes",
                  "More Time for Field Trips",
                  "Sleep Quality Improved",
                  "Stress Level Decreased")
plot_likert(src2b, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

**Please choose the options that best match your feelings of using Food Pantries or CalFresh**

```{r, fig.width=8}
src3m <- bns %>% select(starts_with("SRC3_"))
names(src3m) <- c("Embarrassed to Access Food Pantry",
                  "Grateful to Access Food Panty",
                  "Embarrassed by Having CalFresh",
                  "Grateful for having CalFresh")
plot_likert(src3m, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

# Barriers for Food Pantries

**What is/are the reason(s) for you to not go to campus food pantries or local food banks?**

```{r}
pb <- bns %>% select(PB_Embarrassed,
                     PB_NotAware,
                     PB_NoTime,
                     PB_NoTransportation,
                     PB_FamilyBarrier,
                     PB_DontBelieve,
                     PB_NoLocalLoc,
                     PB_Other)
```

```{r}
names(pb) <- c("Embarrassed",
               "Not Aware",
               "No Time",
               "No Transportation",
               "Family Barrier",
               "Don't Believe",
               "No Local Pantries",
               "Other")
```

```{r}
multi.table(pb) %>% kable(col.names = c("n", "%")) %>% kable_styling()
```

# Habits

**For each of the following statements, indicate how strongly agree or disagree about your current eating and cooking habits**

```{r, fig.width=8}
eh1 <- bns %>% select(starts_with("EH1_"))
names(eh1) <- c("No Access to a Kitchen",
                  "Secure Place to Store Food",
                  "No Room to Store Food",
                  "Thinking about Food is Stressful",
                  "Wish I Had more Food to Eat",
                  "Always Skip Meals",
                  "Don't Cook or Shop for Food",
                  "No One Cooks at Home",
                  "Do Not Think about Habits")
plot_likert(eh1, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

## How many servings of fruits and vegetables do you usually consume per day? 

```{r}
plot_frq(bns$EH2) + xlab("Servings of Fruit and Vegetables")
```

The majority of respondents (n = 101 70.6%) reported that they consume 1-2 servings of fruit and vegetables a day and 16.1% (n = 23) reported that they consume none.

## Drinks (juice, water, alcohol, etc.)

**How many ounces of 100% fruit juices like orange juice, apple juice or grape juice do you consume each day?** 

```{r}
plot_frq(bns$EH3) + xlab("Ounces of 100% Fruit Juice")
```

More than half, or 52.4% (n = 76) of respondents, reported that they drink no 100% fruit juice each day and 34.5% (n = 50) reported that they drink between 1 to 8 ounces a day.

**How many ounces of regular soda, cola, or pop, sports drink, or energy drinks do you consume each day?** 

```{r}
plot_frq(bns$EH4, ylim = c(0,85)) + xlab("Ounces of Soda")
```

Almost half, or 48.6% (n = 71) of respondents, reported that they don't drink any soda each day and 24.0% (n = 35) reported they drink between 1 to 8 ounces a day.

**How many ounces or cups of water or unsweetened clear drinks, such as tea, do you consume each day?** 

```{r}
bns$EH5[bns$EH5 == "24-36 ounces"] <- "25-36 ounces"
bns$EH5_f <- factor(bns$EH5, levels = c("Zero", "1-8 ounces", "9-16 ounces",
                                        "17-24 ounces", "25-36 ounces",
                                        "37-48 ounces", "49-56 ounces",
                                        "57-64 ounces", "65 ounces or more"))
```

```{r}
plot_frq(bns$EH5_f,vjust = "center", y.offset = 3) + xlab("Ounces of Unsweetened Drinks") + coord_flip() + ylim(c(0,40))
```

About 19.0% (n = 27) of respondents reported that they drink 1-8 ounces of water or other unsweetened drinks a day, 7.0% (n = 10) reported they do not drink any ounces of unsweetened drinks a day, and 9.2% (n = 13) reported that they drink more than 65 ounces a day.

**How often do you consume at least one serving of alcohol?** 

```{r}
plot_frq(bns$EH8) + xlab("Alcohol Consumption")
```

Half, or 50.0% (n = 73) of respondents, reported that they do not drink alcohol in a week and 43.1% (n = 63) reported they drink at least one serving of alcohol between 1 to 2 days a week.

**Typically, how many servings of alcohol do you consume when you drink alcohol?** 

```{r}
plot_frq(bns$EH8a, ylim = c(0,45)) + xlab("Servings of Alcohol")
```

More than half, or 54.7% (n = 35) of respondents, reported that when they consume alcohol, they consume between 1 to 2 servings and 26.6% (n = 17) reported that when they consume alcohol, they consume between 3 to 4 servings.


## Dining Out or Meal Replacements

**How frequently do you eat out at family-style or sit-down restaurants/café types of dining establishment per week?** 

```{r}
plot_frq(bns$EH6) + xlab("# of Time Dining Out")
```

38.9% (n = 56) of respondents reported that they do not go out to sit-down restaurants in a week and 45.8% (n = 66) reported that they go out between 1 to 2 times in a week.

**How frequently do you eat from fast food restaurants, convenience stores, or vending machines for a meal or meal replacement?** 

```{r}
plot_frq(bns$EH7) + xlab("# of Time Eating Fast Food")
```

20.5% (n = 30) of respondents reported that they do not eat fast food, from convenience stores, or vending machines in a week and 47.3% (n = 69) reported that they eat fast food between 1 to 2 times a week.



## The following questions pertain to how comfortable you feel about buying or preparing food

```{r, fig.width=8}
eh9 <- bns %>% select(starts_with("EH9_"))
names(eh9) <- c("Use Same Healthy Ingredient in More Than One Meal",
                "Basic Cooking Skills",
                "Buy Healthy Foods on a Budget",
                "Cook Healthy Foods on a Budget")
plot_likert(eh9, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```
















