---
title: "Food Pantry"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}
library(ggplot2)
library(sjPlot)
library(kableExtra)
library(knitr)
library(dplyr)
library(tidyverse)
library(questionr)

load("../data/bns_clean.Rdata")
bns <- out

opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, cache=FALSE, fig.height=4, fig.width=6, fig.align = 'center')
# don't forget when done with sessino to turn CACHE = FALSE and clear knitr cache (last option under the knit button)

# Helper functions to display text answers without blank lines
display.text <- function(data, var){
  data %>% filter(!!as.symbol(var)!="") %>% select(!!as.symbol(var)) %>%
           kable(col.names=NULL) %>% 
           kable_styling(full_width = FALSE, 
           bootstrap_options =c("striped", "responsive", "hover", "condensed"))
}

sjPlot::set_theme(base = theme_bw())
```

# Impact of Pantries

## "For the following questions, please choose how much you agree or disagree with the impact campus food pantries/food banks has or had on your life.

### While I utilize/utilized campus food pantry/pantries or local food bank(s):

```{r, fig.width=8}
src2a <- bns %>% select(starts_with("SRC2a_"))
names(src2a) <- c("Fewer Hours Paid",
                  "More Time Unpaid",
                  "More Money for Bills",
                  "More Money for Entertainment",
                  "Shop More at Farmers' Market",
                  "Learned More about Healthy Foods",
                  "Purchase More Healthy Foods",
                  "Cook More at Home",
                  "Consumed a Healthier Diet",
                  "Consumed Less Fast Food",
                  "Consumed Fewer Processed Foods",
                  "Consumed Fewer Sweetened Beverages",
                  "Consumed Fewer Alcoholic Beverages")
plot_likert(src2a, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE) + theme_bw() + theme(legend.position = "top")
```

```{r, fig.width=8}
src2b <- bns %>% select(starts_with("SRC2b_"))
names(src2b) <- c("Enrolled in More Classes",
                  "Concentrated More in Classes",
                  "Grades have Improved",
                  "More Time to Study for Exams",
                  "More Time to Prepare for Class",
                  "More Time for Homework",
                  "More Time for Office Hours",
                  "More Time to Attend All Classes",
                  "More Time for Field Trips",
                  "Sleep Quality Improved",
                  "Stress Level Decreased")
plot_likert(src2b, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE) + theme_bw() + theme(legend.position = "top")
```

# Barriers for Food Pantries

## What is/are the reason(s) for you to not go to campus food pantries or local food banks?

```{r}
pb <- bns %>% select(PB_Embarrassed,
                     PB_NotAware,
                     PB_NoTime,
                     PB_NoTransportation,
                     PB_FamilyBarrier,
                     PB_DontBelieve,
                     PB_NoLocalLoc,
                     PB_Other)
```

```{r}
names(pb) <- c("Embarrassed",
               "Not Aware",
               "No Time",
               "No Transportation",
               "Family Barrier",
               "Don't Believe",
               "No Local Pantries",
               "Other")
```

```{r}
multi.table(pb) %>% kable(col.names = c("n", "%")) %>% kable_styling()
```

# Habits

## For each of the following statements, indicate how strongly agree or disagree about your current eating and cooking habits

```{r, fig.width=8}
eh1 <- bns %>% select(starts_with("EH1_"))
names(eh1) <- c("No Access to a Kitchen",
                  "Secure Place to Store Food",
                  "No Room to Store Food",
                  "Thinking about Food is Stressful",
                  "Wish I Had more Food to Eat",
                  "Always Skip Meals",
                  "Don't Cook or Shop for Food",
                  "No One Cooks at Home",
                  "Do Not Think about Habits")
plot_likert(eh1, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE) + theme_bw() + theme(legend.position = "top")
```

## How many servings of fruits and vegetables do you usually consume per day? 

```{r}
plot_frq(bns$EH2) + xlab("Servings of Fruit and Vegetables")
```

The majority of respondents (n = 101 70.6%) reported that they consume 1-2 servings of fruit and vegetables a day and 16.1% (n = 23) reported that they consume none.

## How many ounces of 100% fruit juices like orange juice, apple juice or grape juice do you consume each day? 

```{r}
plot_frq(bns$EH3) + xlab("Ounces of 100% Fruit Juice")
```

52.4% (n = 76) of respondents reported that they drink no 100% fruit juice each day and 34.5% (n = 50) reported that they drink between 1 to 8 ounces a day.

## How many ounces of regular soda, cola, or pop, sports drink, or energy drinks do you consume each day? 

```{r}
plot_frq(bns$EH4) + xlab("Ounces of Soda")
```

48.6% (n = 71) of respondents reported that they don't drink any soda each day and 24.0% (n = 35) reported they drink between 1 to 8 ounces a day.

## How many ounces or cups of water or unsweetened clear drinks, such as tea, do you consume each day? 

```{r}
plot_frq(bns$EH5) + xlab("Ounces of Unsweetened Drinks")
```

## How frequently do you eat out at family-style or sit-down restaurants/café types of dining establishment per week? 

```{r}
plot_frq(bns$EH6) + xlab("# of Time Dining Out")
```

38.9% (n = 56) of respondents reported that they do not go out to sit-down restaurants in a week and 45.8% (n = 66) reported that they go out between 1 to 2 times in a week.

## How frequently do you eat from fast food restaurants, convenience stores, or vending machines for a meal or meal replacement? 

```{r}
plot_frq(bns$EH7) + xlab("# of Time Eating Fast Food")
```

20.5% (n = 30) of respondents reported that they do not eat fast food, from convenience stores, or vending machines in a week and 47.3% (n = 69) reported that they eat fast food between 1 to 2 times a week.

## How often do you consume at least one serving of alcohol?  

```{r}
plot_frq(bns$EH8) + xlab("Alcohol Consumption")
```

50.0% (n = 73) of respondents reported that they do not drink alcohol in a week and 43.1% (n = 63) reported they drink at least one serving of alcohol between 1 to 2 days a week.

## Typically, how many servings of alcohol do you consume when you drink alcohol? 

```{r}
plot_frq(bns$EH8a) + xlab("Servings of Alcohol")
```

54.7% (n = 35) of respondents reported that when they consume alcohol, they consume between 1 to 2 servings and 26.6% (n = 17) reported that when they consume alcohol, they consume between 3 to 4 servings.

















