---
title: "Food Pantry"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    css: styles.css
---

```{r, include=FALSE}
source("common_code.R")
sjPlot::set_theme(base = theme_bw())
```


# Impact of Pantries

**For the following questions, please choose how much you agree or disagree with the impact campus food pantries/food banks has or had on your life.**

**While I utilize/utilized campus food pantry/pantries or local food bank(s):**

```{r, fig.width=8, fig.height=8}
src2a <- bns %>% select(starts_with("SRC2a_"))
names(src2a) <- c("Worked Fewer Paid Hours",
                  "More Time for Unpaid Hours",
                  "More Money for Bills",
                  "More Money for Entertainment",
                  "Shop More at Farmers' Market",
                  "Learned More about Healthy Foods",
                  "Purchase More Healthy Foods",
                  "Cook More at Home",
                  "Consumed a Healthier Diet",
                  "Consumed Less Fast Food",
                  "Consumed Fewer Processed Foods",
                  "Consumed Fewer Sweetened Beverages",
                  "Consumed Fewer Alcoholic Beverages")
plot_likert(src2a, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

**While I utilize/utilized campus food pantry/pantries or local food bank(s):** 

```{r, fig.width=8, fig.height=8}
src2b <- bns %>% select(starts_with("SRC2b_"))
names(src2b) <- c("Enrolled in More Classes",
                  "Concentrated More in Classes",
                  "Grades have Improved",
                  "More Time to Study for Exams",
                  "More Time to Prepare for Class",
                  "More Time for Homework",
                  "More Time for Office Hours",
                  "More Time to Attend All Classes",
                  "More Time for Field Trips",
                  "Sleep Quality Improved",
                  "Stress Level Decreased")
plot_likert(src2b, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

**Please choose the options that best match your feelings of using Food Pantries or CalFresh**

```{r, fig.width=8}
src3m <- bns %>% select(starts_with("SRC3_"))
names(src3m) <- c("Embarrassed to Access Food Pantry",
                  "Grateful to Access Food Panty",
                  "Embarrassed by Having CalFresh",
                  "Grateful for having CalFresh")
plot_likert(src3m, 
            grid.range = c(1.2, 1.2),
            expand.grid = FALSE,
            values = "sum.outside",
            show.prc.sign = TRUE, reverse.scale = TRUE) + theme_bw() + theme(legend.position = "top")
```

# Barriers for Food Pantries

**What is/are the reason(s) for you to not go to campus food pantries or local food banks?**

```{r}
pb <- bns %>% select(PB_Embarrassed,
                     PB_NotAware,
                     PB_NoTime,
                     PB_NoTransportation,
                     PB_FamilyBarrier,
                     PB_DontBelieve,
                     PB_NoLocalLoc,
                     PB_Other)
```

```{r}
names(pb) <- c("Embarrassed",
               "Not Aware",
               "No Time",
               "No Transportation",
               "Family Barrier",
               "Don't Believe",
               "No Local Pantries",
               "Other")
```

```{r}
multi.table(pb) %>% kable(col.names = c("n", "%")) %>% kable_styling()
```

