---
title: "Workload"
output: html_document
---

```{r, include=FALSE}
source("common_code.R")
```

# Academic Workload

**How many units (rounded up) are you enrolled in for the current semester at CSU Chico?** 

```{r}
bns$units_relevel <- bns$SD3_1
bns$units_relevel[bns$units_relevel < 12] <- "0-11"
bns$units_relevel[bns$units_relevel > 12 & bns$units_relevel <= 15] <- "13-15"
bns$units_relevel[bns$units_relevel >= 16] <- "16+"
plot_frq(bns$units_relevel, ylim = c(0,100)) + xlab("Units Enrolled")
```

More than half, or 53.7% (n = 80), of students filling out this survey are enrolled in 13-15 units in the semester of the survey, a quarter of the students (24.2% n = 36) are enrolled in 12 units, and 20.8% (n = 31) are enrolled in 16 or more units.

**If currently enrolled at more than one college, how many units (rounded up) are you enrolled in for the current semester at other colleges (NOT CSU Chico)?**

```{r}
bns$outside_units <- bns$SD4_1
bns$outside_units[bns$outside_units <= 3] <- "1-3"
bns$outside_units[bns$outside_units >= 13] <- "13+"
plot_frq(bns$outside_units, vjust=-0.5,  ylim = c(0,4)) + xlab("Units Enrolled Outside CSU Chico")
```

Out of the students who reported they are taking units outside of CSU Chico, about 37.5% (n = 3) are taking 13 or more units in a different college, 25.0% (n = 2) are taking either 1-3 units or 12 units respectively, and only 1 person (12.5%) is enrolled in 10 units outside of CSU Chico.

# Non-Academic Workload

**Estimate the number of hours you work in a PAID job or paid internship per week**

```{r}
bns$paid_hours <- bns$FSI2
bns$paid_hours[bns$paid_hours >= 1 & bns$paid_hours <= 5] <- "1-5"
bns$paid_hours[bns$paid_hours == 6] <- "6-10"
bns$paid_hours[bns$paid_hours == 7] <- "6-10"
bns$paid_hours[bns$paid_hours == 8] <- "6-10"
bns$paid_hours[bns$paid_hours == 9] <- "6-10"
bns$paid_hours[bns$paid_hours == 10] <- "6-10"
bns$paid_hours[bns$paid_hours > 10 & bns$paid_hours <= 15] <- "11-15"
bns$paid_hours[bns$paid_hours > 15 & bns$paid_hours <= 20] <- "16-20"
bns$paid_hours <- factor(bns$paid_hours, labels = c("0", "1-5", "6-10", "11-15", "16-20", "21"))
```

```{r}
plot_frq(bns$paid_hours) + xlab("Paid Hours")
```

The majority of the students in this survey (n = 51 34.2%) reported that they work 0 paid hours a week, roughly 20% (n = 29) reported they work 6-10 paid hours a week and only 4.7% (n = 7) work 1-5 paid hours a week.

**Estimate the number of hours you work in an UNPAID internship or volunteer position**
For example, research with faculty on campus, shadowing a professional or volunteering at a shelter.

```{r}
bns$unpaid_hours <- bns$FSI3
bns$unpaid_hours[bns$unpaid_hours >= 1 & bns$unpaid_hours <= 5] <- "1-5"
bns$unpaid_hours[bns$unpaid_hours == 6] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours == 7] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours == 8] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours == 9] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours == 10] <- "6-10"
bns$unpaid_hours[bns$unpaid_hours > 10 & bns$unpaid_hours <= 15] <- "11-15"
bns$unpaid_hours[bns$unpaid_hours > 15 & bns$unpaid_hours <= 20] <- "16-20"
bns$unpaid_hours <- factor(bns$unpaid_hours, labels = c("0", "1-5", "6-10", "11-15", "16-20", "21"))
```

```{r}
plot_frq(bns$unpaid_hours) + xlab("Unpaid Hours")
```

The majority of respondents (n = 87 58.4%) reported that they work 0 unpaid hours a week, 19.5% (n = 29) work 1-5 unpaid hours, and lastly 12.1% (n = 18) reported they work 21 unpaid hours a week.



